### 2015-08-31 paper.tex
no message

%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}

\usepackage{url}
\urldef{\mailsa}\path|{yilmaz.onur, karagoz,}@metu.edu.tr|    
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{Recommendation Generation for Performance Improvement by using Cross-Organizational Process Mining}

% a short form should be given in case it is too long for the running head
% \titlerunning{Lecture Notes in Computer Science: Authors' Instructions}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Onur Yilmaz \and Pınar Karagoz}
%
%\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Computer Engineering Deperatment, Middle East Technical University, Turkey
\mailsa\\

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

\toctitle{Lecture Notes in Computer Science}
\tocauthor{Authors' Instructions}
\maketitle

\begin{abstract}
The abstract should summarize the contents of the paper and should
contain at least 70 and at most 150 words. It should be written using the
\emph{abstract} environment.
\keywords{We would like to encourage you to list your keywords within
the abstract section}
\end{abstract}

\section{Introduction}

You are strongly encouraged to use \LaTeXe{} for the
preparation of your camera-ready manuscript together with the
corresponding Springer class file \verb+llncs.cls+. Only if you use
\LaTeXe{} can hyperlinks be generated in the online version
of your manuscript.

The \LaTeX{} source of this instruction file for \LaTeX{} users may be
used as a template. This is
located in the ``authors'' subdirectory in
\url{ftp://ftp.springer.de/pub/tex/latex/llncs/latex2e/instruct/} and
entitled \texttt{typeinst.tex}. There is a separate package for Word 
users. Kindly send the final and checked source
and PDF files of your paper to the Contact Volume Editor. This is
usually one of the organizers of the conference. You should make sure
that the \LaTeX{} and the PDF files are identical and correct and that
only one version of your paper is sent. It is not possible to update
files at a later stage. Please note that we do not need the printed
paper.

We would like to draw your attention to the fact that it is not possible
to modify a paper in any way, once it has been published. This applies
to both the printed book and the online version of the publication.
Every detail, including the order of the names of the authors, should
be checked before the paper is sent to the Volume Editors.

\subsection{Checking the PDF File}

Kindly assure that the Contact Volume Editor is given the name and email
address of the contact author for your paper. The Contact Volume Editor
uses these details to compile a list for our production department at
SPS in India. Once the files have been worked upon, SPS sends a copy of
the final pdf of each paper to its contact author. The contact author is
asked to check through the final pdf to make sure that no errors have
crept in during the transfer or preparation of the files. This should
not be seen as an opportunity to update or copyedit the papers, which is
not possible due to time constraints. Only errors introduced during the
preparation of the files will be corrected.

This round of checking takes place about two weeks after the files have
been sent to the Editorial by the Contact Volume Editor, i.e., roughly
seven weeks before the start of the conference for conference
proceedings, or seven weeks before the volume leaves the printer's, for
post-proceedings. If SPS does not receive a reply from a particular
contact author, within the timeframe given, then it is presumed that the
author has found no errors in the paper. The tight publication schedule
of LNCS does not allow SPS to send reminders or search for alternative
email addresses on the Internet.

In some cases, it is the Contact Volume Editor that checks all the final
pdfs. In such cases, the authors are not involved in the checking phase.

\subsection{Additional Information Required by the Volume Editor}

If you have more than one surname, please make sure that the Volume Editor
knows how you are to be listed in the author index.

\subsection{Copyright Forms}

The copyright form may be downloaded from the ``For Authors"
(Information for LNCS Authors) section of the LNCS Website:
\texttt{www.springer.com/lncs}. Please send your signed copyright form
to the Contact Volume Editor, either as a scanned pdf or by fax or by
courier. One author may sign on behalf of all of the other authors of a
particular paper. Digital signatures are acceptable.

\section{Paper Preparation}

Springer provides you with a complete integrated \LaTeX{} document class
(\texttt{llncs.cls}) for multi-author books such as those in the LNCS
series. Papers not complying with the LNCS style will be reformatted.
This can lead to an increase in the overall number of pages. We would
therefore urge you not to squash your paper.

Please always cancel any superfluous definitions that are
not actually used in your text. If you do not, these may conflict with
the definitions of the macro package, causing changes in the structure
of the text and leading to numerous mistakes in the proofs.

If you wonder what \LaTeX{} is and where it can be obtained, see the
``\textit{LaTeX project site}'' (\url{http://www.latex-project.org})
and especially the webpage ``\textit{How to get it}''
(\url{http://www.latex-project.org/ftp.html}) respectively.

When you use \LaTeX\ together with our document class file,
\texttt{llncs.cls},
your text is typeset automatically in Computer Modern Roman (CM) fonts.
Please do
\emph{not} change the preset fonts. If you have to use fonts other
than the preset fonts, kindly submit these with your files.

Please use the commands \verb+\label+ and \verb+\ref+ for
cross-references and the commands \verb+\bibitem+ and \verb+\cite+ for
references to the bibliography, to enable us to create hyperlinks at
these places.

For preparing your figures electronically and integrating them into
your source file we recommend using the standard \LaTeX{} \verb+graphics+ or
\verb+graphicx+ package. These provide the \verb+\includegraphics+ command.
In general, please refrain from using the \verb+\special+ command.

Remember to submit any further style files and
fonts you have used together with your source files.

\subsubsection{Headings.}

Headings should be capitalized
(i.e., nouns, verbs, and all other words
except articles, prepositions, and conjunctions should be set with an
initial capital) and should,
with the exception of the title, be aligned to the left.
Words joined by a hyphen are subject to a special rule. If the first
word can stand alone, the second word should be capitalized.

Here are some examples of headings: ``Criteria to Disprove
Context-Freeness of Collage Language", ``On Correcting the Intrusion of
Tracing Non-deterministic Programs by Software", ``A User-Friendly and
Extendable Data Distribution System", ``Multi-flip Networks:
Parallelizing GenSAT", ``Self-determinations of Man".

\subsubsection{Lemmas, Propositions, and Theorems.}

The numbers accorded to lemmas, propositions, and theorems, etc. should
appear in consecutive order, starting with Lemma 1, and not, for
example, with Lemma 11.

\subsection{Figures}

For \LaTeX\ users, we recommend using the \emph{graphics} or \emph{graphicx}
package and the \verb+\includegraphics+ command.

Please check that the lines in line drawings are not
interrupted and are of a constant width. Grids and details within the
figures must be clearly legible and may not be written one on top of
the other. Line drawings should have a resolution of at least 800 dpi
(preferably 1200 dpi). The lettering in figures should have a height of
2~mm (10-point type). Figures should be numbered and should have a
caption which should always be positioned \emph{under} the figures, in
contrast to the caption belonging to a table, which should always appear
\emph{above} the table; this is simply achieved as matter of sequence in
your source.

Please center the figures or your tabular material by using the \verb+\centering+
declaration. Short captions are centered by default between the margins
and typeset in 9-point type (Fig.~\ref{fig:example} shows an example).
The distance between text and figure is preset to be about 8~mm, the
distance between figure and caption about 6~mm.

To ensure that the reproduction of your illustrations is of a reasonable
quality, we advise against the use of shading. The contrast should be as
pronounced as possible.

If screenshots are necessary, please make sure that you are happy with
the print quality before you send the files.
\begin{figure}
\centering
\includegraphics[height=6.2cm]{eijkel2}
\caption{One kernel at $x_s$ (\emph{dotted kernel}) or two kernels at
$x_i$ and $x_j$ (\textit{left and right}) lead to the same summed estimate
at $x_s$. This shows a figure consisting of different types of
lines. Elements of the figure described in the caption should be set in
italics, in parentheses, as shown in this sample caption.}
\label{fig:example}
\end{figure}

Please define figures (and tables) as floating objects. Please avoid
using optional location parameters like ``\verb+[h]+" for ``here".

\paragraph{Remark 1.}

In the printed volumes, illustrations are generally black and white
(halftones), and only in exceptional cases, and if the author is
prepared to cover the extra cost for color reproduction, are colored
pictures accepted. Colored pictures are welcome in the electronic
version free of charge. If you send colored figures that are to be
printed in black and white, please make sure that they really are
legible in black and white. Some colors as well as the contrast of
converted colors show up very poorly when printed in black and white.

\subsection{Formulas}

Displayed equations or formulas are centered and set on a separate
line (with an extra line or halfline space above and below). Displayed
expressions should be numbered for reference. The numbers should be
consecutive within each section or within the contribution,
with numbers enclosed in parentheses and set on the right margin --
which is the default if you use the \emph{equation} environment, e.g.,
\begin{equation}
  \psi (u) = \int_{o}^{T} \left[\frac{1}{2}
  \left(\Lambda_{o}^{-1} u,u\right) + N^{\ast} (-u)\right] dt \;  .
\end{equation}

Equations should be punctuated in the same way as ordinary
text but with a small space before the end punctuation mark.

\subsection{Footnotes}

The superscript numeral used to refer to a footnote appears in the text
either directly after the word to be discussed or -- in relation to a
phrase or a sentence -- following the punctuation sign (comma,
semicolon, or period). Footnotes should appear at the bottom of
the
normal text area, with a line of about 2~cm set
immediately above them.\footnote{The footnote numeral is set flush left
and the text follows with the usual word spacing.}

\subsection{Program Code}

Program listings or program commands in the text are normally set in
typewriter font, e.g., CMTT10 or Courier.

\medskip

\noindent
{\it Example of a Computer Program}
\begin{verbatim}
program Inflation (Output)
  {Assuming annual inflation rates of 7%, 8%, and 10%,...
   years};
   const
     MaxYears = 10;
   var
     Year: 0..MaxYears;
     Factor1, Factor2, Factor3: Real;
   begin
     Year := 0;
     Factor1 := 1.0; Factor2 := 1.0; Factor3 := 1.0;
     WriteLn('Year  7% 8% 10%'); WriteLn;
     repeat
       Year := Year + 1;
       Factor1 := Factor1 * 1.07;
       Factor2 := Factor2 * 1.08;
       Factor3 := Factor3 * 1.10;
       WriteLn(Year:5,Factor1:7:3,Factor2:7:3,Factor3:7:3)
     until Year = MaxYears
end.
\end{verbatim}
%
\noindent
{\small (Example from Jensen K., Wirth N. (1991) Pascal user manual and
report. Springer, New York)}

\subsection{Citations}

For citations in the text please use
square brackets and consecutive numbers: \cite{jour}, \cite{lncschap},
\cite{proceeding1} -- provided automatically
by \LaTeX 's \verb|\cite| \dots\verb|\bibitem| mechanism.

\subsection{Page Numbering and Running Heads}

There is no need to include page numbers. If your paper title is too
long to serve as a running head, it will be shortened. Your suggestion
as to how to shorten it would be most welcome.

\section{LNCS Online}

The online version of the volume will be available in LNCS Online.
Members of institutes subscribing to the Lecture Notes in Computer
Science series have access to all the pdfs of all the online
publications. Non-subscribers can only read as far as the abstracts. If
they try to go beyond this point, they are automatically asked, whether
they would like to order the pdf, and are given instructions as to how
to do so.

Please note that, if your email address is given in your paper,
it will also be included in the meta data of the online version.

\section{BibTeX Entries}

The correct BibTeX entries for the Lecture Notes in Computer Science
volumes can be found at the following Website shortly after the
publication of the book:
\url{http://www.informatik.uni-trier.de/~ley/db/journals/lncs.html}

\subsubsection*{Acknowledgments.} The heading should be treated as a
subsubsection heading and should not be assigned a number.

\section{The References Section}\label{references}

In order to permit cross referencing within LNCS-Online, and eventually
between different publishers and their online databases, LNCS will,
from now on, be standardizing the format of the references. This new
feature will increase the visibility of publications and facilitate
academic research considerably. Please base your references on the
examples below. References that don't adhere to this style will be
reformatted by Springer. You should therefore check your references
thoroughly when you receive the final pdf of your paper.
The reference section must be complete. You may not omit references.
Instructions as to where to find a fuller version of the references are
not permissible.

We only accept references written using the latin alphabet. If the title
of the book you are referring to is in Russian or Chinese, then please write
(in Russian) or (in Chinese) at the end of the transcript or translation
of the title.

The following section shows a sample reference list with entries for
journal articles \cite{jour}, an LNCS chapter \cite{lncschap}, a book
\cite{book}, proceedings without editors \cite{proceeding1} and
\cite{proceeding2}, as well as a URL \cite{url}.
Please note that proceedings published in LNCS are not cited with their
full titles, but with their acronyms!

\begin{thebibliography}{4}

\bibitem{jour} Smith, T.F., Waterman, M.S.: Identification of Common Molecular
Subsequences. J. Mol. Biol. 147, 195--197 (1981)

\bibitem{lncschap} May, P., Ehrlich, H.C., Steinke, T.: ZIB Structure Prediction Pipeline:
Composing a Complex Biological Workflow through Web Services. In: Nagel,
W.E., Walter, W.V., Lehner, W. (eds.) Euro-Par 2006. LNCS, vol. 4128,
pp. 1148--1158. Springer, Heidelberg (2006)

\bibitem{book} Foster, I., Kesselman, C.: The Grid: Blueprint for a New Computing
Infrastructure. Morgan Kaufmann, San Francisco (1999)

\bibitem{proceeding1} Czajkowski, K., Fitzgerald, S., Foster, I., Kesselman, C.: Grid
Information Services for Distributed Resource Sharing. In: 10th IEEE
International Symposium on High Performance Distributed Computing, pp.
181--184. IEEE Press, New York (2001)

\bibitem{proceeding2} Foster, I., Kesselman, C., Nick, J., Tuecke, S.: The Physiology of the
Grid: an Open Grid Services Architecture for Distributed Systems
Integration. Technical report, Global Grid Forum (2002)

\bibitem{url} National Center for Biotechnology Information, \url{http://www.ncbi.nlm.nih.gov}

\end{thebibliography}

\section*{Appendix: Springer-Author Discount}

LNCS authors are entitled to a 33.3\% discount off all Springer
publications. Before placing an order, the author should send an email, 
giving full details of his or her Springer publication,
to \url{orders-HD-individuals@springer.com} to obtain a so-called token. This token is a
number, which must be entered when placing an order via the Internet, in
order to obtain the discount.

\section{Checklist of Items to be Sent to Volume Editors}
Here is a checklist of everything the volume editor requires from you:

\begin{itemize}
\settowidth{\leftmargin}{{\Large$\square$}}\advance\leftmargin\labelsep
\itemsep8pt\relax
\renewcommand\labelitemi{{\lower1.5pt\hbox{\Large$\square$}}}

\item The final \LaTeX{} source files
\item A final PDF file
\item A copyright form, signed by one author on behalf of all of the
authors of the paper.
\item A readme giving the name and email address of the
corresponding author.
\end{itemize}
\end{document}

### 2015-08-31 paper.tex
no message

@@
 \usepackage{graphicx}
-
 \usepackage{url}
-\urldef{\mailsa}\path|{yilmaz.onur, karagoz,}@metu.edu.tr|    
+\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
+\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|  
 \newcommand{\keywords}[1]{\par\addvspace\baselineskip
@@
 % unless you accept that it will be published
-\institute{Computer Engineering Deperatment, Middle East Technical University, Turkey
+\institute{Computer Engineering Deperatment, Middle East Technical University, Turkey}
 \mailsa\\
+\mailsc\\
+\url{http://ceng.metu.edu.tr}
 
@@
 
-\toctitle{Lecture Notes in Computer Science}
-\tocauthor{Authors' Instructions}
-\maketitle
+% \toctitle{Lecture Notes in Computer Science}
+% \tocauthor{Authors' Instructions}
+% \maketitle
 

### 2015-08-31 paper.tex
no message

--- 2015-08-31 paper.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% This is the LaTeX source for the instructions to authors using
-% the LaTeX document class 'llncs.cls' for contributions to
-% the Lecture Notes in Computer Sciences series.
-% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
-%
-% It may be used as a template for your own input - copy it
-% to a new file with a new name and use it as the basis
-% for your article.
-%
-% NB: the document class 'llncs' has its own and detailed documentation, see
-% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \documentclass[runningheads,a4paper]{llncs}
 
-\usepackage{amssymb}
-\setcounter{tocdepth}{3}
+\usepackage[american]{babel}
+
 \usepackage{graphicx}
 
-\usepackage{url}
-\urldef{\mailsa}\path|{yilmaz.onur, karagoz,}@metu.edu.tr|    
-\newcommand{\keywords}[1]{\par\addvspace\baselineskip
-\noindent\keywordname\enspace\ignorespaces#1}
+%extended enumerate, such as \begin{compactenum}
+\usepackage{paralist}
+
+%put figures inside a text
+%\usepackage{picins}
+%use
+%\piccaptioninside
+%\piccaption{...}
+%\parpic[r]{\includegraphics ...}
+%Text...
+
+%Sorts the citations in the brackets
+%\usepackage{cite}
+
+%for easy quotations: \enquote{text}
+\usepackage{csquotes}
+
+\usepackage[T1]{fontenc}
+
+%enable margin kerning
+\usepackage{microtype}
+
+%better font, similar to the default springer font
+\usepackage[%
+rm={oldstyle=false,proportional=true},%
+sf={oldstyle=false,proportional=true},%
+tt={oldstyle=false,proportional=true,variable=true},%
+qt=false%
+]{cfr-lm}
+%
+%if more space is needed, exchange cfr-lm by mathptmx
+%\usepackage{mathptmx}
+
+%for demonstration purposes only
+\usepackage[math]{blindtext}
+
+\usepackage[
+%pdfauthor={},
+%pdfsubject={},
+%pdftitle={},
+%pdfkeywords={},
+bookmarks=false,
+breaklinks=true,
+colorlinks=true,
+linkcolor=black,
+citecolor=black,
+urlcolor=black,
+%pdfstartpage=19,
+pdfpagelayout=SinglePage
+]{hyperref}
+%enables correct jumping to figures when referencing
+\usepackage[all]{hypcap}
+
+\usepackage[capitalise,nameinlink]{cleveref}
+%Nice formats for \cref
+\crefname{section}{Sect.}{Sect.}
+\Crefname{section}{Section}{Sections}
+\crefname{figure}{Fig.}{Fig.}
+\Crefname{figure}{Figure}{Figures}
+
+\usepackage{xspace}
+%\newcommand{\eg}{e.\,g.\xspace}
+%\newcommand{\ie}{i.\,e.\xspace}
+\newcommand{\eg}{e.\,g.,\ }
+\newcommand{\ie}{i.\,e.,\ }
+
+%introduce \powerset - hint by http://matheplanet.com/matheplanet/nuke/html/viewtopic.php?topic=136492&post_id=997377
+\DeclareFontFamily{U}{MnSymbolC}{}
+\DeclareSymbolFont{MnSyC}{U}{MnSymbolC}{m}{n}
+\DeclareFontShape{U}{MnSymbolC}{m}{n}{
+    <-6>  MnSymbolC5
+   <6-7>  MnSymbolC6
+   <7-8>  MnSymbolC7
+   <8-9>  MnSymbolC8
+   <9-10> MnSymbolC9
+  <10-12> MnSymbolC10
+  <12->   MnSymbolC12%
+}{}
+\DeclareMathSymbol{\powerset}{\mathord}{MnSyC}{180}
+
+% correct bad hyphenation here
+\hyphenation{op-tical net-works semi-conduc-tor}
 
@@
 
-\mainmatter  % start of an individual contribution
+%Works on MiKTeX only
+%hint by http://goemonx.blogspot.de/2012/01/pdflatex-ligaturen-und-copynpaste.html
+%also http://tex.stackexchange.com/questions/4397/make-ligatures-in-linux-libertine-copyable-and-searchable
+%This allows a copy'n'paste of the text from the paper
+\input glyphtounicode.tex
+\pdfgentounicode=1
 
-% first the title is needed
 \title{Recommendation Generation for Performance Improvement by using Cross-Organizational Process Mining}
+%If Title is too long, use \titlerunning
+%\titlerunning{Short Title}
 
-% a short form should be given in case it is too long for the running head
-% \titlerunning{Lecture Notes in Computer Science: Authors' Instructions}
+%Single insitute
+\author{Onur Yılmaz \and Pınar Karagöz}
+%If there are too many authors, use \authorrunning
+%\authorrunning{First Author et al.}
+\institute{Computer Engineering Department, Middle East Technical University, Turkey}
+\email{yilmaz.onur@metu.edu.tr}\and \email{karagoz@ceng.metu.edu.tr}
+%Multiple insitutes
+%Currently disabled
+%
+\iffalse
+%Multiple institutes are typeset as follows:
+\author{Firstname Lastname\inst{1} \and Firstname Lastname\inst{2} }
+%If there are too many authors, use \authorrunning
+%\authorrunning{First Author et al.}
 
-% the name(s) of the author(s) follow(s) next
-%
-% NB: Chinese authors should write their first names(s) in front of
-% their surnames. This ensures that the names appear correctly in
-% the running heads and the author index.
-%
-\author{Onur Yilmaz \and Pınar Karagoz}
-%
-%\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
-% (feature abused for this document to repeat the title also on left hand pages)
+\institute{
+Insitute 1\\
+\email{...}\and
+Insitute 2\\
+\email{...}
+}
+\fi
 
-% the affiliations are given next; don't give your e-mail address
-% unless you accept that it will be published
-\institute{Computer Engineering Deperatment, Middle East Technical University, Turkey
-\mailsa\\
-
-%
-% NB: a more complex sample for affiliations and the mapping to the
-% corresponding authors can be found in the file "llncs.dem"
-% (search for the string "\mainmatter" where a contribution starts).
-% "llncs.dem" accompanies the document class "llncs.cls".
-%
-
-\toctitle{Lecture Notes in Computer Science}
-\tocauthor{Authors' Instructions}
 \maketitle
@@
 \begin{abstract}
-The abstract should summarize the contents of the paper and should
-contain at least 70 and at most 150 words. It should be written using the
-\emph{abstract} environment.
-\keywords{We would like to encourage you to list your keywords within
-the abstract section}
+Abstract goes here
 \end{abstract}
 
-\section{Introduction}
+\keywords{...}
 
-You are strongly encouraged to use \LaTeXe{} for the
-preparation of your camera-ready manuscript together with the
-corresponding Springer class file \verb+llncs.cls+. Only if you use
-\LaTeXe{} can hyperlinks be generated in the online version
-of your manuscript.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}\label{sec:intro}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blindtext
 
-The \LaTeX{} source of this instruction file for \LaTeX{} users may be
-used as a template. This is
-located in the ``authors'' subdirectory in
-\url{ftp://ftp.springer.de/pub/tex/latex/llncs/latex2e/instruct/} and
-entitled \texttt{typeinst.tex}. There is a separate package for Word 
-users. Kindly send the final and checked source
-and PDF files of your paper to the Contact Volume Editor. This is
-usually one of the organizers of the conference. You should make sure
-that the \LaTeX{} and the PDF files are identical and correct and that
-only one version of your paper is sent. It is not possible to update
-files at a later stage. Please note that we do not need the printed
-paper.
+Winery~\cite{Winery} is graphical modeling tool.
 
-We would like to draw your attention to the fact that it is not possible
-to modify a paper in any way, once it has been published. This applies
-to both the printed book and the online version of the publication.
-Every detail, including the order of the names of the authors, should
-be checked before the paper is sent to the Volume Editors.
-
-\subsection{Checking the PDF File}
-
-Kindly assure that the Contact Volume Editor is given the name and email
-address of the contact author for your paper. The Contact Volume Editor
-uses these details to compile a list for our production department at
-SPS in India. Once the files have been worked upon, SPS sends a copy of
-the final pdf of each paper to its contact author. The contact author is
-asked to check through the final pdf to make sure that no errors have
-crept in during the transfer or preparation of the files. This should
-not be seen as an opportunity to update or copyedit the papers, which is
-not possible due to time constraints. Only errors introduced during the
-preparation of the files will be corrected.
-
-This round of checking takes place about two weeks after the files have
-been sent to the Editorial by the Contact Volume Editor, i.e., roughly
-seven weeks before the start of the conference for conference
-proceedings, or seven weeks before the volume leaves the printer's, for
-post-proceedings. If SPS does not receive a reply from a particular
-contact author, within the timeframe given, then it is presumed that the
-author has found no errors in the paper. The tight publication schedule
-of LNCS does not allow SPS to send reminders or search for alternative
-email addresses on the Internet.
-
-In some cases, it is the Contact Volume Editor that checks all the final
-pdfs. In such cases, the authors are not involved in the checking phase.
-
-\subsection{Additional Information Required by the Volume Editor}
-
-If you have more than one surname, please make sure that the Volume Editor
-knows how you are to be listed in the author index.
-
-\subsection{Copyright Forms}
-
-The copyright form may be downloaded from the ``For Authors"
-(Information for LNCS Authors) section of the LNCS Website:
-\texttt{www.springer.com/lncs}. Please send your signed copyright form
-to the Contact Volume Editor, either as a scanned pdf or by fax or by
-courier. One author may sign on behalf of all of the other authors of a
-particular paper. Digital signatures are acceptable.
-
-\section{Paper Preparation}
-
-Springer provides you with a complete integrated \LaTeX{} document class
-(\texttt{llncs.cls}) for multi-author books such as those in the LNCS
-series. Papers not complying with the LNCS style will be reformatted.
-This can lead to an increase in the overall number of pages. We would
-therefore urge you not to squash your paper.
-
-Please always cancel any superfluous definitions that are
-not actually used in your text. If you do not, these may conflict with
-the definitions of the macro package, causing changes in the structure
-of the text and leading to numerous mistakes in the proofs.
-
-If you wonder what \LaTeX{} is and where it can be obtained, see the
-``\textit{LaTeX project site}'' (\url{http://www.latex-project.org})
-and especially the webpage ``\textit{How to get it}''
-(\url{http://www.latex-project.org/ftp.html}) respectively.
-
-When you use \LaTeX\ together with our document class file,
-\texttt{llncs.cls},
-your text is typeset automatically in Computer Modern Roman (CM) fonts.
-Please do
-\emph{not} change the preset fonts. If you have to use fonts other
-than the preset fonts, kindly submit these with your files.
-
-Please use the commands \verb+\label+ and \verb+\ref+ for
-cross-references and the commands \verb+\bibitem+ and \verb+\cite+ for
-references to the bibliography, to enable us to create hyperlinks at
-these places.
-
-For preparing your figures electronically and integrating them into
-your source file we recommend using the standard \LaTeX{} \verb+graphics+ or
-\verb+graphicx+ package. These provide the \verb+\includegraphics+ command.
-In general, please refrain from using the \verb+\special+ command.
-
-Remember to submit any further style files and
-fonts you have used together with your source files.
-
-\subsubsection{Headings.}
-
-Headings should be capitalized
-(i.e., nouns, verbs, and all other words
-except articles, prepositions, and conjunctions should be set with an
-initial capital) and should,
-with the exception of the title, be aligned to the left.
-Words joined by a hyphen are subject to a special rule. If the first
-word can stand alone, the second word should be capitalized.
-
-Here are some examples of headings: ``Criteria to Disprove
-Context-Freeness of Collage Language", ``On Correcting the Intrusion of
-Tracing Non-deterministic Programs by Software", ``A User-Friendly and
-Extendable Data Distribution System", ``Multi-flip Networks:
-Parallelizing GenSAT", ``Self-determinations of Man".
-
-\subsubsection{Lemmas, Propositions, and Theorems.}
-
-The numbers accorded to lemmas, propositions, and theorems, etc. should
-appear in consecutive order, starting with Lemma 1, and not, for
-example, with Lemma 11.
-
-\subsection{Figures}
-
-For \LaTeX\ users, we recommend using the \emph{graphics} or \emph{graphicx}
-package and the \verb+\includegraphics+ command.
-
-Please check that the lines in line drawings are not
-interrupted and are of a constant width. Grids and details within the
-figures must be clearly legible and may not be written one on top of
-the other. Line drawings should have a resolution of at least 800 dpi
-(preferably 1200 dpi). The lettering in figures should have a height of
-2~mm (10-point type). Figures should be numbered and should have a
-caption which should always be positioned \emph{under} the figures, in
-contrast to the caption belonging to a table, which should always appear
-\emph{above} the table; this is simply achieved as matter of sequence in
-your source.
-
-Please center the figures or your tabular material by using the \verb+\centering+
-declaration. Short captions are centered by default between the margins
-and typeset in 9-point type (Fig.~\ref{fig:example} shows an example).
-The distance between text and figure is preset to be about 8~mm, the
-distance between figure and caption about 6~mm.
-
-To ensure that the reproduction of your illustrations is of a reasonable
-quality, we advise against the use of shading. The contrast should be as
-pronounced as possible.
-
-If screenshots are necessary, please make sure that you are happy with
-the print quality before you send the files.
 \begin{figure}
-\centering
-\includegraphics[height=6.2cm]{eijkel2}
-\caption{One kernel at $x_s$ (\emph{dotted kernel}) or two kernels at
-$x_i$ and $x_j$ (\textit{left and right}) lead to the same summed estimate
-at $x_s$. This shows a figure consisting of different types of
-lines. Elements of the figure described in the caption should be set in
-italics, in parentheses, as shown in this sample caption.}
-\label{fig:example}
+Simple Figure
+\caption{Simple Figure}
+\label{fig:simple}
 \end{figure}
 
-Please define figures (and tables) as floating objects. Please avoid
-using optional location parameters like ``\verb+[h]+" for ``here".
+\begin{table}
+\caption{Simple Table}
 
-\paragraph{Remark 1.}
+\label{tab:simple}
+Simple Table
+\end{table}
 
-In the printed volumes, illustrations are generally black and white
-(halftones), and only in exceptional cases, and if the author is
-prepared to cover the extra cost for color reproduction, are colored
-pictures accepted. Colored pictures are welcome in the electronic
-version free of charge. If you send colored figures that are to be
-printed in black and white, please make sure that they really are
-legible in black and white. Some colors as well as the contrast of
-converted colors show up very poorly when printed in black and white.
+cref Demonstration: Cref at beginning of sentence, cref in all other cases.
 
-\subsection{Formulas}
+\Cref{fig:simple} shows a simple fact, although \cref{fig:simple} could also show something else.
 
-Displayed equations or formulas are centered and set on a separate
-line (with an extra line or halfline space above and below). Displayed
-expressions should be numbered for reference. The numbers should be
-consecutive within each section or within the contribution,
-with numbers enclosed in parentheses and set on the right margin --
-which is the default if you use the \emph{equation} environment, e.g.,
-\begin{equation}
-  \psi (u) = \int_{o}^{T} \left[\frac{1}{2}
-  \left(\Lambda_{o}^{-1} u,u\right) + N^{\ast} (-u)\right] dt \;  .
-\end{equation}
+\Cref{tab:simple} shows a simple fact, although \cref{tab:simple} could also show something else.
 
-Equations should be punctuated in the same way as ordinary
-text but with a small space before the end punctuation mark.
+\Cref{sec:intro} shows a simple fact, although \cref{sec:intro} could also show something else.
 
-\subsection{Footnotes}
+Brackets work as designed:
+<test>
 
-The superscript numeral used to refer to a footnote appears in the text
-either directly after the word to be discussed or -- in relation to a
-phrase or a sentence -- following the punctuation sign (comma,
-semicolon, or period). Footnotes should appear at the bottom of
-the
-normal text area, with a line of about 2~cm set
-immediately above them.\footnote{The footnote numeral is set flush left
-and the text follows with the usual word spacing.}
+The symbol for powerset is now correct: $\powerset$ and not a Weierstrass p ($\wp$).
 
-\subsection{Program Code}
+\begin{inparaenum}
+\item All these items...
+\item ...appear in one line
+\item This is enabled by the paralist package.
+\end{inparaenum}
 
-Program listings or program commands in the text are normally set in
-typewriter font, e.g., CMTT10 or Courier.
+``something in quotes'' using plain tex or use \enquote{the enquote command}.
 
-\medskip
+\section{Conclusion and Outlook}
 
-\noindent
-{\it Example of a Computer Program}
-\begin{verbatim}
-program Inflation (Output)
-  {Assuming annual inflation rates of 7%, 8%, and 10%,...
-   years};
-   const
-     MaxYears = 10;
-   var
-     Year: 0..MaxYears;
-     Factor1, Factor2, Factor3: Real;
-   begin
-     Year := 0;
-     Factor1 := 1.0; Factor2 := 1.0; Factor3 := 1.0;
-     WriteLn('Year  7% 8% 10%'); WriteLn;
-     repeat
-       Year := Year + 1;
-       Factor1 := Factor1 * 1.07;
-       Factor2 := Factor2 * 1.08;
-       Factor3 := Factor3 * 1.10;
-       WriteLn(Year:5,Factor1:7:3,Factor2:7:3,Factor3:7:3)
-     until Year = MaxYears
-end.
-\end{verbatim}
-%
-\noindent
-{\small (Example from Jensen K., Wirth N. (1991) Pascal user manual and
-report. Springer, New York)}
+\subsubsection*{Acknowledgments}
+...
 
-\subsection{Citations}
+In the bibliography, use \texttt{\textbackslash textsuperscript} for ``st'', ``nd'', ...:
+E.g., \enquote{The 2\textsuperscript{nd} conference on examples}.
 
-For citations in the text please use
-square brackets and consecutive numbers: \cite{jour}, \cite{lncschap},
-\cite{proceeding1} -- provided automatically
-by \LaTeX 's \verb|\cite| \dots\verb|\bibitem| mechanism.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliographystyle{splncs03}
+\bibliography{paper}
 
-\subsection{Page Numbering and Running Heads}
+All links were last followed on October 5, 2014.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-There is no need to include page numbers. If your paper title is too
-long to serve as a running head, it will be shortened. Your suggestion
-as to how to shorten it would be most welcome.
-
-\section{LNCS Online}
-
-The online version of the volume will be available in LNCS Online.
-Members of institutes subscribing to the Lecture Notes in Computer
-Science series have access to all the pdfs of all the online
-publications. Non-subscribers can only read as far as the abstracts. If
-they try to go beyond this point, they are automatically asked, whether
-they would like to order the pdf, and are given instructions as to how
-to do so.
-
-Please note that, if your email address is given in your paper,
-it will also be included in the meta data of the online version.
-
-\section{BibTeX Entries}
-
-The correct BibTeX entries for the Lecture Notes in Computer Science
-volumes can be found at the following Website shortly after the
-publication of the book:
-\url{http://www.informatik.uni-trier.de/~ley/db/journals/lncs.html}
-
-\subsubsection*{Acknowledgments.} The heading should be treated as a
-subsubsection heading and should not be assigned a number.
-
-\section{The References Section}\label{references}
-
-In order to permit cross referencing within LNCS-Online, and eventually
-between different publishers and their online databases, LNCS will,
-from now on, be standardizing the format of the references. This new
-feature will increase the visibility of publications and facilitate
-academic research considerably. Please base your references on the
-examples below. References that don't adhere to this style will be
-reformatted by Springer. You should therefore check your references
-thoroughly when you receive the final pdf of your paper.
-The reference section must be complete. You may not omit references.
-Instructions as to where to find a fuller version of the references are
-not permissible.
-
-We only accept references written using the latin alphabet. If the title
-of the book you are referring to is in Russian or Chinese, then please write
-(in Russian) or (in Chinese) at the end of the transcript or translation
-of the title.
-
-The following section shows a sample reference list with entries for
-journal articles \cite{jour}, an LNCS chapter \cite{lncschap}, a book
-\cite{book}, proceedings without editors \cite{proceeding1} and
-\cite{proceeding2}, as well as a URL \cite{url}.
-Please note that proceedings published in LNCS are not cited with their
-full titles, but with their acronyms!
-
-\begin{thebibliography}{4}
-
-\bibitem{jour} Smith, T.F., Waterman, M.S.: Identification of Common Molecular
-Subsequences. J. Mol. Biol. 147, 195--197 (1981)
-
-\bibitem{lncschap} May, P., Ehrlich, H.C., Steinke, T.: ZIB Structure Prediction Pipeline:
-Composing a Complex Biological Workflow through Web Services. In: Nagel,
-W.E., Walter, W.V., Lehner, W. (eds.) Euro-Par 2006. LNCS, vol. 4128,
-pp. 1148--1158. Springer, Heidelberg (2006)
-
-\bibitem{book} Foster, I., Kesselman, C.: The Grid: Blueprint for a New Computing
-Infrastructure. Morgan Kaufmann, San Francisco (1999)
-
-\bibitem{proceeding1} Czajkowski, K., Fitzgerald, S., Foster, I., Kesselman, C.: Grid
-Information Services for Distributed Resource Sharing. In: 10th IEEE
-International Symposium on High Performance Distributed Computing, pp.
-181--184. IEEE Press, New York (2001)
-
-\bibitem{proceeding2} Foster, I., Kesselman, C., Nick, J., Tuecke, S.: The Physiology of the
-Grid: an Open Grid Services Architecture for Distributed Systems
-Integration. Technical report, Global Grid Forum (2002)
-
-\bibitem{url} National Center for Biotechnology Information, \url{http://www.ncbi.nlm.nih.gov}
-
-\end{thebibliography}
-
-\section*{Appendix: Springer-Author Discount}
-
-LNCS authors are entitled to a 33.3\% discount off all Springer
-publications. Before placing an order, the author should send an email, 
-giving full details of his or her Springer publication,
-to \url{orders-HD-individuals@springer.com} to obtain a so-called token. This token is a
-number, which must be entered when placing an order via the Internet, in
-order to obtain the discount.
-
-\section{Checklist of Items to be Sent to Volume Editors}
-Here is a checklist of everything the volume editor requires from you:
-
-\begin{itemize}
-\settowidth{\leftmargin}{{\Large$\square$}}\advance\leftmargin\labelsep
-\itemsep8pt\relax
-\renewcommand\labelitemi{{\lower1.5pt\hbox{\Large$\square$}}}
-
-\item The final \LaTeX{} source files
-\item A final PDF file
-\item A copyright form, signed by one author on behalf of all of the
-authors of the paper.
-\item A readme giving the name and email address of the
-corresponding author.
-\end{itemize}
 \end{document}

### 2015-08-31 1_introduction/introduction.tex
no message

\section{Introduction}\label{sec:intro}
Process mining is a relatively young and developing research area with the roots in computational intelligence, data mining; and process modeling and analysis \cite{van2012process}. Main idea in this research area is to discover, monitor and improve processes by extracting information from event logs. With this idea, process mining creates a bridge between data mining and business process modeling and analysis. Interest in this research area has two origins; firstly, events are recorded and easily available in the modern information systems. Secondly, highly competitive and rapidly changing business life requires improvement and support for business processes \cite{van2012process}. Traditional process mining approaches work on a single organization; however, with the increase of cloud computing and shared infrastructures, event logs of multiple organizations are currently available for analysis. In principle, there are two main environments where cross-organizational process mining stands out. Firstly, when organizations work together to execute the same process, it is insufficient to analyze only logs of one organization and gathered information from all stakeholders should be merged prior to analysis. Secondly, organizations essentially execute the same processes with different needs and configurations on a common infrastructure, where cross-organizational process mining can help the organizations to learn from each other's experience, knowledge and processes.

### 2015-08-31 paper.tex
no message

@@
 %Single insitute
-\author{Onur Yılmaz \and Pınar Karagöz}
+\author{Onur Yilmaz \and Pinar Karagoz}
 %If there are too many authors, use \authorrunning
@@
 \institute{Computer Engineering Department, Middle East Technical University, Turkey}
-\email{yilmaz.onur@metu.edu.tr}\and \email{karagoz@ceng.metu.edu.tr}
+%\email{yilmaz.onur@metu.edu.tr} 
+%\email{karagoz@ceng.metu.edu.tr}
 %Multiple insitutes
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}\label{sec:intro}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blindtext
+\input{1_introduction/introduction.tex}
 
-Winery~\cite{Winery} is graphical modeling tool.
-
-\begin{figure}
-Simple Figure
-\caption{Simple Figure}
-\label{fig:simple}
-\end{figure}
-
-\begin{table}
-\caption{Simple Table}
-
-\label{tab:simple}
-Simple Table
-\end{table}
-
-cref Demonstration: Cref at beginning of sentence, cref in all other cases.
-
-\Cref{fig:simple} shows a simple fact, although \cref{fig:simple} could also show something else.
-
-\Cref{tab:simple} shows a simple fact, although \cref{tab:simple} could also show something else.
-
-\Cref{sec:intro} shows a simple fact, although \cref{sec:intro} could also show something else.
-
-Brackets work as designed:
-<test>
-
-The symbol for powerset is now correct: $\powerset$ and not a Weierstrass p ($\wp$).
-
-\begin{inparaenum}
-\item All these items...
-\item ...appear in one line
-\item This is enabled by the paralist package.
-\end{inparaenum}
-
-``something in quotes'' using plain tex or use \enquote{the enquote command}.
-
-\section{Conclusion and Outlook}
-
-\subsubsection*{Acknowledgments}
-...
-
-In the bibliography, use \texttt{\textbackslash textsuperscript} for ``st'', ``nd'', ...:
-E.g., \enquote{The 2\textsuperscript{nd} conference on examples}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliographystyle{splncs03}
-\bibliography{paper}
-
-All links were last followed on October 5, 2014.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliography{references/references}
 

### 2015-08-31 1_introduction/introduction.tex
no message

@@
-\section{Introduction}\label{sec:intro}
+\section{Introduction}
+\label{sec:intro}
+
 Process mining is a relatively young and developing research area with the roots in computational intelligence, data mining; and process modeling and analysis \cite{van2012process}.

### 2015-08-31 1_introduction/introduction.tex
no message

@@
 \section{Introduction}
-\label{sec:intro}
+\label{sec:introduction}
 
@@
 Main idea in this research area is to discover, monitor and improve processes by extracting information from event logs.
-With this idea, process mining creates a bridge between data mining and business process modeling and analysis.
-Interest in this research area has two origins; firstly, events are recorded and easily available in the modern information systems.
-Secondly, highly competitive and rapidly changing business life requires improvement and support for business processes \cite{van2012process}.
-Traditional process mining approaches work on a single organization; however, with the increase of cloud computing and shared infrastructures, event logs of multiple organizations are currently available for analysis.
-In principle, there are two main environments where cross-organizational process mining stands out.
-Firstly, when organizations work together to execute the same process, it is insufficient to analyze only logs of one organization and gathered information from all stakeholders should be merged prior to analysis.
-Secondly, organizations essentially execute the same processes with different needs and configurations on a common infrastructure, where cross-organizational process mining can help the organizations to learn from each other's experience, knowledge and processes.
+Traditional process mining approaches work on a single organization; however, with the increase of cloud computing and shared infrastructures, event logs of multiple organizations are currently available for analysis where cross-organizational process mining stands out.
+In cross-organizational process mining area, recent studies focus on commonality and collaboration between organizations.
+Studies focus on how similar the process models and behaviors of organizations under cross comparison \cite{buijs2012towards} and challenges based on partitioning of tasks and process models between organizations \cite{van2011intra}.
+This study is based on the environment where processes are executed on several organizations and cross-organizational process mining is applied with the idea of unsupervised learning where predictor variables related to performances of organizations are used.
+
+The approach proposed in this thesis is a four-stage solution and it starts with mining the process models of organizations; followed by performance indicator analysis and then mismatch pattern analysis.
+Finally recommendation generation stage is undertaken to create learning opportunities for each organization.
+With this approach it is aimed to help business process management users to focus on the potentially important parts of their business maps.
+Proposed methodology is implemented in ProM framework \cite{verbeek2010prom} as a set of plugins corresponding for each stage and packaged under the name of \textit{CrossOrgProcMin} and tested on a synthetic and real-life event logs.
+Performance of methodology is assessed with a defined evaluation metrics for each stage and resulting recommendations are presented to show how this approach helps users to focus on learning opportunities between organizations with a performance improvement potential.
+
+The rest of the paper is organized as follows:
+\begin{itemize}
+	\item In Chapter~\ref{sec:relatedwork}, related studies in process mining area are presented. 
+	\item In Chapter~\ref{sec:background}, background information for the relevant topics is explained.
+	\item In Chapter~\ref{sec:methodology}, methodology proposed in this study is presented with detail.
+	\item In Chapter~\ref{sec:results-and-discussions}, methodology of this study is applied on datasets and results are discussed.
+	\item In Chapter~\ref{sec:conclusion-and-future-work}, summary of this study is presented with the final remarks and pointers for future work. 
+\end{itemize}

### 2015-08-31 paper.tex
no message

@@
 \begin{abstract}
-Abstract goes here
+Process mining is a relatively young and developing research area with the main idea of discovering, monitoring and improving processes by extracting information from the event logs.
+With the increase of cloud computing and shared infrastructures, event logs of multiple organizations are available for analysis where cross-organizational process mining stands with the opportunity for organizations learning from each other.
+The approach proposed in this study mines process models of organizations and calculates performance indicators; followed by clustering of organizations based on performance indicators and finally spots mismatches between the process models to generate recommendations.
+This approach is implemented as extensible and configurable plugin set in ProM framework and tested by synthetic and real life logs where successful and suitable results are achieved within evaluation metrics.
+Generated recommendation results indicate that the use of this approach considerably helps users to focus on the areas of process models with potential performance improvement, which are difficult to spot manually and visually.
 \end{abstract}
 
-\keywords{...}
+\keywords{Process Mining, Cross-organizational Process Mining, Recommendation Generation, Process Performance Improvement}
 

### 2015-08-31 1_introduction/introduction.tex
no message

@@
 The rest of the paper is organized as follows:
-\begin{itemize}
-	\item In Chapter~\ref{sec:relatedwork}, related studies in process mining area are presented. 
-	\item In Chapter~\ref{sec:background}, background information for the relevant topics is explained.
-	\item In Chapter~\ref{sec:methodology}, methodology proposed in this study is presented with detail.
-	\item In Chapter~\ref{sec:results-and-discussions}, methodology of this study is applied on datasets and results are discussed.
-	\item In Chapter~\ref{sec:conclusion-and-future-work}, summary of this study is presented with the final remarks and pointers for future work. 
-\end{itemize}
+\begin{inparaenum}
+	\item In Section~\ref{sec:relatedwork}, related studies in process mining area are presented. 
+	\item In Section~\ref{sec:background}, background information for the relevant topics is explained.
+	\item In Section~\ref{sec:methodology}, methodology proposed in this study is presented with detail.
+	\item In Section~\ref{sec:results-and-discussions}, methodology of this study is applied on datasets and results are discussed.
+	\item In Section~\ref{sec:conclusion-and-future-work}, summary of this study is presented with the final remarks and pointers for future work. 
+\end{inparaenum}

### 2015-08-31 2_relatedwork/relatedwork.tex
no message

\section{Related Work}
\label{sec:relatedwork}

In this section, studies related to the work presented in this thesis are summarized. Firstly, studies in the process mining area are explained and then studies from cross-organizational process mining, which is the main topic of this research, is introduced. Following these, studies related to similarity in process mining is mentioned. Finally, performance and conformance analysis approaches in process mining area are presented.

### 2015-08-31 1_introduction/introduction.tex
no message

@@
 
-The approach proposed in this thesis is a four-stage solution and it starts with mining the process models of organizations; followed by performance indicator analysis and then mismatch pattern analysis.
+The approach proposed in this study is a four-stage solution and it starts with mining the process models of organizations; followed by performance indicator analysis and then mismatch pattern analysis.
 Finally recommendation generation stage is undertaken to create learning opportunities for each organization.

### 2015-08-31 2_relatedwork/relatedwork.tex
no message

@@
 Finally, performance and conformance analysis approaches in process mining area are presented.
+
+ Within the process mining framework, there are various different process mining algorithms proposed which have the same aim of discovering underlying processes.
+Considering the underlying approaches undertaken, algorithms can be grouped as $\alpha$-algorithms \cite{van2004workflow, de2004process}, inductive approaches \cite{herbst1998integrating, herbst2000dealing}, hierarchical clustering \cite{greco2005mining}, genetic approaches \cite{van2005genetic, esgin2010hybrid}, and heuristic approaches \cite{esgin2009hybrid}.
+Considering the scope of this study; process discovery operations are undertaken with inductive methods which is a robust, repeatable and mature set of approaches.

### 2015-08-31 2_relatedwork/relatedwork.tex
no message

--- 2015-08-31 2_relatedwork/relatedwork.tex
@@
 Finally, performance and conformance analysis approaches in process mining area are presented.
+
+ Within the process mining framework, there are various different process mining algorithms proposed which have the same aim of discovering underlying processes.
+Considering the underlying approaches undertaken, algorithms can be grouped as $\alpha$-algorithms \cite{van2004workflow,de2004process}, inductive approaches \cite{herbst1998integrating, herbst2000dealing}, hierarchical clustering \cite{greco2005mining}, genetic approaches \cite{van2005genetic,esgin2010hybrid}, and heuristic approaches \cite{esgin2009hybrid}.
+Considering the scope of this study; process discovery operations are undertaken with inductive methods which is a robust, repeatable and mature set of approaches.

### 2015-08-31 2_relatedwork/relatedwork.tex
no message

--- 2015-08-31 2_relatedwork/relatedwork.tex
@@
 Finally, performance and conformance analysis approaches in process mining area are presented.
+
+ Within the process mining framework, there are various different process mining algorithms proposed which have the same aim of discovering underlying processes.
+Considering the underlying approaches undertaken, algorithms can be grouped as $\alpha$-algorithms \cite{van2004workflow,de2004process}, inductive approaches \cite{herbst1998integrating,herbst2000dealing}, hierarchical clustering \cite{greco2005mining}, genetic approaches \cite{van2005genetic,esgin2010hybrid}, and heuristic approaches \cite{esgin2009hybrid}.
+Considering the scope of this study; process discovery operations are undertaken with inductive methods which is a robust, repeatable and mature set of approaches.

### 2015-08-31 2_relatedwork/relatedwork.tex
no message

@@
 Considering the scope of this study; process discovery operations are undertaken with inductive methods which is a robust, repeatable and mature set of approaches.
+
+Cross-organizational mining is based on cross-correlation of workflows and the realized activities in different organization to compare processes and their performances of different organizational units in an objective approach.
+In the study of Bujis et al.
+\cite{buijs2012towards}, process models and behaviors of organizations are cross-compared with the idea of supporting and representing.
+In the studies of van der Aalst \cite{van2011business,van2011intra}, configurable process models for the organizations sharing the same infrastructure and doing the similar work is proposed with the ideas of \textit{exploiting commonality} and \textit{collaboration}.
+Notion of this study is based on \textit{exploiting commonality} where organizations can learn from each other.
+
+Similarity in process mining have various approaches which focus on metrics \cite{dijkman2011similarity}, analytical comparison \cite{buijs2014comparing}, delta analysis \cite{esgin2011delta,esgin2013sequence} and mismatch patterns \cite{dijkman2007mismatch}.
+In this research, combination of metric and mismatch pattern approaches are used to identify variations between process models of different organizations.

### 2015-09-03 3_background/background.tex
no message

\section{Background}
\label{sec:background}

In this section background information is presented for the relevant topics to this thesis study. Process discovery approaches and then performance analysis methodologies are presented.Finally, mismatch patterns in process models are presented. All topics in this chapter are limited to the scope of this thesis study with the aim of constructing a necessary background.

\subsection{Process Discovery}
\label{subsec:process-discovery}
In process mining field, one of the most challenging tasks is to construct a process model based on the behavior in the event logs, namely process discovery. Many process discovery algorithms are proposed to address different challenges in process discovery and using different notations. However, in this study focus of the study is learning from the cross-organizational process mining rather than addressing all process discovery challenges. With this reasoning, Inductive Process Mining \cite{leemans2013discovering} is selected as appropriate since it is simple, highly applicable and configurable. In the literature, its derivatives which handles infrequent behaviors \cite{leemans2014discoveringinfrequent}; incomplete logs \cite{leemans2014discoveringincomplete}; and model optimization \cite{weidlich2012profiles} are also available. \textit{Inductive Miner Infrequent (IMi)} \cite{leemans2014discoveringinfrequent} extension is capable of handling noise in the event logs. By filtering the infrequent behavior, it is aimed that \textit{IMi} succeeds with improved models discovered. After each recursive step of \textit{IM}, filtering is applied if the discovered model is a flower model which represents infrequent behavior. Basic idea behind filtering is setting a user-defined threshold between 0 to 1 and with the help of this threshold, both log splittings and mining operations are done on a cleaner subset of logs. When the discovered models compared to \textit{IM}, \textit{IMi} results with lower fitness, higher precision and equal generalization.

\subsection{Process Performance Analysis}
\label{subsec:process-performance-analysis}

\subsection{Mismatch Patterns in Process Models}
\label{subsec:mismatch-patterns-in-process-models}

### 2015-09-03 3_background/background.tex
no message

@@
 
-\subsection{Process Discovery}
-\label{subsec:process-discovery}
 In process mining field, one of the most challenging tasks is to construct a process model based on the behavior in the event logs, namely process discovery.
@@
 In the literature, its derivatives which handles infrequent behaviors \cite{leemans2014discoveringinfrequent}; incomplete logs \cite{leemans2014discoveringincomplete}; and model optimization \cite{weidlich2012profiles} are also available.
-\textit{Inductive Miner Infrequent (IMi)} \cite{leemans2014discoveringinfrequent} extension is capable of handling noise in the event logs.
-By filtering the infrequent behavior, it is aimed that \textit{IMi} succeeds with improved models discovered.
-After each recursive step of \textit{IM}, filtering is applied if the discovered model is a flower model which represents infrequent behavior.
-Basic idea behind filtering is setting a user-defined threshold between 0 to 1 and with the help of this threshold, both log splittings and mining operations are done on a cleaner subset of logs.
-When the discovered models compared to \textit{IM}, \textit{IMi} results with lower fitness, higher precision and equal generalization.
+\textit{Inductive Miner Infrequent (IMi)} \cite{leemans2014discoveringinfrequent} extension is used in this study which is capable of filtering the infrequent behavior and results with lower fitness, higher precision and equal generalization.
 

### 2015-09-03 3_background/background.tex
no message

@@
 In this section background information is presented for the relevant topics to this thesis study.
-Process discovery approaches and then performance analysis methodologies are presented.Finally, mismatch patterns in process models are presented.
+Process discovery approaches and then mismatch patterns in process models are presented.
 All topics in this chapter are limited to the scope of this thesis study with the aim of constructing a necessary background.
@@
 
-\subsection{Process Performance Analysis}
-\label{subsec:process-performance-analysis}
+In cross-organizational process mining environment, there is a need to align processes of different organizations and in this scope both the organizations and their processes are similar but have significant differences.
+In order to align these processes and organizations, there is a need for spotting differences between process models.
+In the study of Dijkman \cite{dijkman2007mismatch}, a collection of patterns to describe frequent mismatches between the similar process models are presented.
+Mismatch patterns are grouped into three as authorization, activity and control flow mismatch patterns.
+Authorization mismatch patterns are based on assignment of the same tasks to different roles in different processes and left outside the scope of this thesis.
+Activity mismatch patterns are based on representing the tasks of a process by a different collection of activities in a different process, or not representing at all.
+Within the scope of this study, the related activity mismatch patterns are defined in study \cite{dijkman2007mismatch} as follows:
+\begin{description}
+  \item[Skipped Activity] An activity exists in one process but no equivalent activity is found in the other process as illustrated in Figure~\ref{fig:skipped-activity}.
+      \begin{figure}
+      \centering
+      \includegraphics[width=\textwidth]{3_background/mismatch-patterns-skipped-activity}
+      \caption{Example of Skipped Activity Pattern}
+      \label{fig:skipped-activity}
+      \end{figure}
+  \item[Refined Activity] An activity exists in one process but, as an equivalent, a collection of activities are existing in the other process to achieve the same task.
+An illustration is provided in Figure~\ref{fig:refined-activity}.
+      \begin{figure}
+      \centering
+      \includegraphics[width=\textwidth]{3_background/mismatch-patterns-refined-activity}
+      \caption{Example of Refined Activity Pattern}
+      \label{fig:refined-activity}
+      \end{figure}
+\end{description}
 
-\subsection{Mismatch Patterns in Process Models}
-\label{subsec:mismatch-patterns-in-process-models}
+Control flow mismatch patterns are based on using different control-flow relations and dependencies for the same activities in different processes.
+Within the scope of this thesis study, the following related control flow mismatch patterns are defined as given in \cite{dijkman2007mismatch}:
+\begin{description}
+  \item[Activities at Different Moments in Processes] Set of activities are undertaken with different orders in different processes as shown in Figure~\ref{fig:different-moments}. 
+      \begin{figure}
+      \centering
+      \includegraphics[width=\textwidth]{3_background/mismatch-patterns-different-moments}
+      \caption{Example of Activities at Different Moments in Process Pattern}
+      \label{fig:different-moments}
+      \end{figure}
+  \item[Different Conditions for Occurrence] Set of dependencies are same for two processes; however, occurrence condition is different.
+An example is provided in Figure~\ref{fig:different-conditions}.
+      \begin{figure}
+      \centering
+      \includegraphics[width=\textwidth]{3_background/mismatch-patterns-different-conditions}
+      \caption{Example of Different Conditions for Occurrence Pattern}
+      \label{fig:different-conditions}
+      \end{figure}
+  \item[Different Dependencies] Dependency set of activities differ in different organizations. An example of this pattern is shown in Figure~\ref{fig:different-dependency}.
+      \begin{figure}
+      \centering
+      \includegraphics[width=\textwidth]{3_background/mismatch-patterns-different-dependency}
+      \caption{Example of Different Dependencies Pattern}
+      \label{fig:different-dependency}
+      \end{figure}
+  \item[Additional Dependencies] This pattern is a special case of different dependencies where one set of activities includes the other and results with additional dependencies as illustrated in Figure~\ref{fig:additional-dependency}.
+      \begin{figure}
+      \centering
+      \includegraphics[width=\textwidth]{3_background/mismatch-patterns-additional-dependency}
+      \caption{Example of Additional Dependencies Pattern}
+      \label{fig:additional-dependency}
+      \end{figure}
+\end{description}
+
+As mentioned in the study \cite{dijkman2007mismatch}, their approach does not create a comprehensive list to resolve all mismatches but the most common ones spotted during case studies.
+In addition, from their definitions and examples it can be easily seen that these patterns are not orthogonal.
+Moreover, there are no algorithms provided to spot these mismatches in \cite{dijkman2007mismatch} or consequent studies, and thus implementation of spotting mismatch patterns are kept within the scope of this thesis study.

### 2015-09-03 3_background/background.tex
no message

--- 2015-09-03 3_background/background.tex
@@
 
-\subsection{Process Performance Analysis}
-\label{subsec:process-performance-analysis}
+In cross-organizational process mining environment, there is a need to align processes of different organizations and in this scope both the organizations and their processes are similar but have significant differences.
+In order to align these processes and organizations, there is a need for spotting differences between process models.
+In the study of Dijkman \cite{dijkman2007mismatch}, a collection of patterns to describe frequent mismatches between the similar process models are presented.Within the scope of this study, the related mismatch patterns are defined in study \cite{dijkman2007mismatch} as follows:
+\begin{description}
+  \item[Skipped Activity] An activity exists in one process but no equivalent activity is found in the other process.
+  \item[Refined Activity] An activity exists in one process but, as an equivalent, a collection of activities are existing in the other process to achieve the same task.
+  \item[Activities at Different Moments in Processes] Set of activities are undertaken with different orders in different processes.
+  \item[Different Conditions for Occurrence] Set of dependencies are same for two processes; however, occurrence condition is different.
+  \item[Different Dependencies] Dependency set of activities differ in different organizations.
+  \item[Additional Dependencies] This pattern is a special case of different dependencies where one set of activities includes the other and results with additional dependencies.
+\end{description}
 
-\subsection{Mismatch Patterns in Process Models}
-\label{subsec:mismatch-patterns-in-process-models}
+As mentioned in the study \cite{dijkman2007mismatch}, their approach does not create a comprehensive list to resolve all mismatches but the most common ones spotted during case studies.
+In addition, from their definitions and examples it can be easily seen that these patterns are not orthogonal.
+Moreover, there are no algorithms provided to spot these mismatches in \cite{dijkman2007mismatch} or consequent studies, and thus implementation of spotting mismatch patterns are kept within the scope of this study.

### 2015-09-07 4_methodology/methodology.tex
no message

\section{Methodology}
\label{sec:methodology}
In this section, the methodology proposed in this study is presented. Firstly, approach overview is described from a high-level perspective. Then, each stage in the methodology is presented together with their importance in the study, mathematical representations and definitions; and black-box diagrams. In the last section of this chapter, implementation details of this methodology in ProM framework is explained in detail with a software architecture overview.

\subsection{Approach Overview}
\label{subsec:approach-overview}
The approach proposed in this study consists of four main stages visualized in Figure~\ref{fig:approach-overview}. Firstly, in \textit{Process Model Mining}, process models are extracted from event logs for each organization with a user specified noise threshold. Secondly, in \textit{Performance Indicator Analysis}, event logs are replayed on process models and performance indicators are calculated for each organization then using these indicators, organizations are clustered based on how well they are operating. Thirdly, in \textit{Mismatch Pattern Analysis}, differences between process models of organizations are extracted with well-established mismatch patterns. Finally, in \textit{Recommendation Generation}, using the performance indicator clusterings and differences between process models, a set of recommendations for each organization is generated. In the following sections, each stage will be explained in detail with their mathematical backgrounds.

### 2015-09-07 4_methodology/methodology.tex
no message

@@
 In the following sections, each stage will be explained in detail with their mathematical backgrounds.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{4_methodology/approach-overview}
+  \caption{Overview of Methodology}
+  \label{fig:approach-overview}
+\end{figure}
+
+\subsection{Process Model Mining}
+\label{subsec:process-model-mining}
+Process model mining in the proposed approach has the aim of creating reproducible and generalized process models from event logs.
+In order to achieve this aim, implementation of \textit{Inductive Miner Infrequent (IMi)}, which is proposed in \cite{leemans2014discoveringinfrequent} as an extension to \textit{Inductive Miner} to handle noise in the event logs, is used in this study.
+Considering the scope of this study, instead of computational details of \textit{Inductive Miner Infrequent (IMi)}; black-box representation is used to explain its usage in the methodology.
+In order to set a filtering threshold, a user-provided value between 0 to 1 is added as input to method in addition to event logs.
+As a result, workflow net is produced which is a sound and properly completed Petri net without deadlocks.
+Black-box of this stage is illustrated in Figure~\ref{fig:process-model-mining-blackbox} and this stage is called for every organization's event logs to create their own process models in Workflow net formalization.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{4_methodology/process-model-mining-blackbox}
+  \caption{Process Model Mining Stage as Black-box }
+  \label{fig:process-model-mining-blackbox}
+\end{figure}
+
+\subsection{Performance Indicator Analysis}
+\label{subsec:performance-indicator-analysis}
+Performance indicator analysis stage focuses on calculating and analyzing the performance values using the event logs and mined process models. This stage consists of mainly two concepts as 
+\begin{inparaenum}[\itshape a\upshape)]
+\item alignment and calculation of performance indicators; and
+\item clustering of organizations based on their performance values.
+\end{inparaenum}
+In order to evaluate the performance of an organization based on their process models and past activities; there is a number of indicators in time dimension, cost dimension and utilization \cite{van2011process}.
+However, in this study, process related performance values are considered since differences in the process models are studied in the next stages.
+With this reasoning, the following performance indicators are calculated and analyzed in this stage of methodology:
+\begin{description}
+	\item[Average Time Between Activities] For each activity in the process model, average time to reach other activity is calculated.
+This is a simple but powerful performance metric for organizations since it can yield the average time to complete one task based on a starting point.
+From the performance perspective, organizations want to minimize average time between activities to increase their throughput \cite{van2012replaying}.
+	\item[Standard Deviation of Time Between Activities] Time between activities in real life is not stable and they deviate due to various reasons such as people responsible of tasks, size and the content of tasks or seasonality \cite{van2011process}.
+On the other hand, organizations want to be confident about their processes and therefore they want to minimize the deviation in the time between activities.
+Minimized deviation in time helps organizations to plan, act and re-organize the activities in the processes with high accuracy \cite{van2012replaying}.
+\end{description}

### 2015-09-07 4_methodology/methodology.tex
no message

@@
   \centering
-  \includegraphics[width=\textwidth]{4_methodology/process-model-mining-blackbox}
+  \includegraphics[width=0.5\textwidth]{4_methodology/process-model-mining-blackbox}
   \caption{Process Model Mining Stage as Black-box }
@@
 \end{description}
+
+\subsubsection{Replay and Performance Indicator Calculation}
+\label{subsubsec:replay-and-performance-summary}
+Replay of event logs on process models is based on the idea of \textit{alignment} which is formalized in \cite{van2012replaying} and the basic assumption in this concept is that process models and event logs have the same activity labels.
+Alignment is based on \textit{moves in the model and log} and in order to have a successful replay where optimal alignment should be achieved.
+As proposed in \cite{adriansyah2011conformance, adriansyah2011towards}, $A^{*}$ algorithm which is a path-finding algorithm based on graphs is used to find optimal alignment of event logs on the process models.
+With the generated and user-specified inputs, replay and performance indicator calculation in the methodology can be visualized in Figure~\ref{fig:replay-and-performance-indicator-calculation}.
+For each organization, the steps in the diagram are followed with the corresponding event logs and process models; and the resulting process summaries are used for further analysis.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{4_methodology/replay-and-performance-indicator-calculation}
+  \caption{Replay and Performance Indicator Calculation Stage as Black-box}
+  \label{fig:replay-and-performance-indicator-calculation}
+\end{figure}
+
+\subsubsection{Performance Indicator Clustering}
+\label{subsubsec:performance-indicator-clustering}
+
+Clustering is based on the idea of collecting the set of observations into clusters so that observations within the same cluster are similar whereas the observations from different clusters are dissimilar.
+In this thesis study, clustering is used to gather organizations based on their performance indicator data.
+In this study, a generic approach based on centroid-based clustering is exploited.
+For the fixed number of \textit{k} clusters, the approach is well-known as \textit{k-means clustering}.
+Considering the popularity of this approach and its extensions, random initialization based \textit{k-means++} approach from the study of Arthur and Vassilvitskii \cite{arthur2007} is used to cluster organizations.
+For each organization, \textit{Performance Summary} data is used as the data source in clustering.
+Since number of clusters are not known priori, k-means clustering is applied starting \textit{k} from 1 to the number of organizations.
+For each clustering with different number of clusters, SSE values are plotted and user is made to select the appropriate cluster size.
+For the selected cluster size, clustering related information is used to generate recommendations in the further steps.
+This stage of methodology can be visualized as an input-output system in Figure~\ref{fig:performance-indicator-clustering-blackbox}.
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{4_methodology/performance-indicator-clustering-blackbox}
+  \caption{Performance Indicator Clustering Stage as Black-box }
+  \label{fig:performance-indicator-clustering-blackbox}
+\end{figure}

### 2015-09-07 4_methodology/methodology.tex
no message

@@
 Alignment is based on \textit{moves in the model and log} and in order to have a successful replay where optimal alignment should be achieved.
-As proposed in \cite{adriansyah2011conformance, adriansyah2011towards}, $A^{*}$ algorithm which is a path-finding algorithm based on graphs is used to find optimal alignment of event logs on the process models.
+As proposed in \cite{adriansyah2011conformance,adriansyah2011towards}, $A^{*}$ algorithm which is a path-finding algorithm based on graphs is used to find optimal alignment of event logs on the process models.
 With the generated and user-specified inputs, replay and performance indicator calculation in the methodology can be visualized in Figure~\ref{fig:replay-and-performance-indicator-calculation}.

### 2015-09-07 4_methodology/methodology.tex
no message

@@
 \end{figure}
+
+\subsection{Mismatch Pattern Analysis}
+\label{subsec:mismatch-pattern-analysis}
+In order to learn from other organizations, it is necessary to spot the differences between process models of different organizations.
+In this phase of methodology, differences between process models will be revealed by the mismatch patterns which are defined by Dijkman \cite{dijkman2007mismatch}.
+In the process mining stage, process models are mined to create Workflow nets; however, mismatch pattern definitions are closer to business environment and it is more suitable spot patterns in BPMN notation.
+Thus, mined process models are converted to BPMN models and then mismatch pattern analysis is applied.
+After spotting differences, mismatch patterns for activities and control flows are revealed for the organizations.
+
+Business Process Modeling Notation (BPMN) is one of the widely accepted modeling language in the industry and its a standardized notation by the Object Management Group (OMG) since 2004.
+In this stage, BPMN formulation is used since mismatch patterns have roots in real-life business environment \cite{dijkman2007mismatch}.
+
+For each organization, mined process models are converted to BPMN models and mismatch patterns analysis is undertaken on them, in order to locate differences between two process models or cluster of process models.
+In addition, since performance indicators are calculated based on a starting and ending points in the process model, same approach is applied to locate mismatch patterns.
+In other words, differences of process models are located through a starting activity to an ending activity.
+When the complete set of mismatches between process models are required, this approach is used with starting and ending points as source and sink activities.
+For each organization, mismatch patterns are gathered and stored for the further analysis as visualized in Figure~\ref{fig:mismatch-pattern-analysis-blackbox}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{4_methodology/mismatch-pattern-analysis-blackbox}
+  \caption{Mismatch Pattern Analysis Stage as Black-box}
+  \label{fig:mismatch-pattern-analysis-blackbox}
+\end{figure}
+
+\subsection{Recommendation Generation}
+\label{subsec:recommendation-generation}
+Recommendation generation stage in the methodology is the final and core stage where all information retrieved from event logs until now are utilized.
+In this study, idea of recommendation is based on providing a set of mismatch patterns for each organization so that they can enhance their processes.
+These mismatch patterns are generated by comparing the process models of other organizations, particularly which are performing better in terms of their performance indicator values.
+In addition, clustering of organizations is undertaken to generalize the way of identifying which organizations perform better in this environment.
+
+Algorithm of recommendation generation function is based on the idea of checking other clusters for a significant change in performance indicators, where significance is defined by the threshold provided by user.
+After finding significant difference, all organizations in other clusters are checked against mismatch patterns with the starting and ending activities defined in performance indicators.
+With this constraining, only mismatches which are located between the activities that causes high level of difference in performance indicators are analyzed.
+
+This stage of methodology can be visualized as gathering inputs of mismatch patterns data and cluster analysis data in Figure~\ref{fig:recommendation-generation-blackox}.
+In addition, a performance difference threshold is gathered from the user to specify how much difference between clusters is necessary to check for mismatch patterns and generate recommendations.
+This stage generates recommendation data for each organization which contains a set of mismatch patterns.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\textwidth]{4_methodology/recommendation-generation-blackbox}
+  \caption{Recommendation Generation Stage as Black-box}
+  \label{fig:recommendation-generation-blackox}
+\end{figure}
+
+\subsection{Implementation in ProM Framework}
+\label{subsec:implementation}
+Methodology of this thesis study is implemented in ProM \cite{verbeek2010prom}, which is an extensible framework that supports a wide variety of process mining techniques in form of plugins.
+ProM is an open source framework for process mining algorithms which provides a platform to users and developers.
+Aim of this framework is to create a standard process mining platform that is accepted in industry and academia with an active community.
+Approach of this thesis study is implemented with its each stage as a standalone plugin that enables extensions for further studies.
+Developed set of plugins are packaged with the name of \textit{CrossOrgProcMin}\footnote{\url{http://www.promtools.org/prom6/packages/CrossOrgProcMin}} and published open-source\footnote{\url{http://github.com/onuryilmaz/cross-org-proc-min}} being available in the latest version of ProM release.
+
+Approach of this study is divided into stand-alone stages where inputs and outputs between them are defined strictly.
+With the help of this understanding, each stage is developed as a stand-alone plug-in in ProM framework which can be called separately.
+For this aim, five plug-ins are developed which are visualized in Figure~\ref{fig:architecture} to provide a high-level perspective.
+In addition, a set of utilities are developed to visualize and persistence of data in ProM environment.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{4_methodology/architecture}
+  \caption{Software Architecture for  Cross-Organizational Process Miner}
+  \label{fig:architecture}
+\end{figure}

### 2015-09-07 5_results_discussions/results_discussions.tex
no message

\section{Results and Discussions}
\label{sec:results-and-discussions}

In this section, methodology presented in this study is applied on datasets and results are presented. Firstly, evaluation metrics are defined for each stage of methodology to assess the performance of approach. Following this, methodology is applied on two datasets and results are explained with discussions.

Approach in this study is an aggregation of various methods and they are significantly different from each other in their mathematical background. Therefore, instead of a global evaluation metric for the complete methodology, each stage will be evaluated within its evaluation metrics. Since these stages are executed sequentially, it is important for each stage to perform well enough to yield a successful outcome. Evaluation metrics for each stage are as follows:

\begin{description}
	\item[Process Model Mining] Performance of process mining stage is measured by \textit{Fitness} and \textit{Appropriateness} which are defined in \cite{rozinat2008conformance}.
	\item[Performance Indicator Analysis] In replay phase, \textit{alignment costs} \cite{van2012replaying}  are compared with process model mining metrics. In clustering phase, within-SSE analysis is undertaken to decide on the number of clusters.
	\item[Mismatch Pattern Analysis] In this stage, number of mismatch patterns found are compared with the \textit{graph-edit similarity} \cite{dijkman2011similarity} of process models.
	\item[Recommendation Generation] In recommendation generation, different threshold values are tried to check how many mismatch patterns are generated for organizations and how they could be used for focused analysis.
\end{description}

Cross-organizational mining aims to find cross-correlation of workflows and activities in different organizations and this yields the necessity of organizations that do the same main activity with comparable process flows. Considering these characteristics, there are few dataset available in the literature that are well-structured, documented and valuable. In this thesis study, one synthetic and one real-life event log datasets are presented and used in the following sections to evaluate the performance of the proposed methodology.

\begin{description}
  \item[Loan Application Process \cite{loan-app-data}] This synthetically created dataset consists of event log variants of a simple loan application in a financial institute. This dataset includes artificial event logs of 4 variants where each variant includes different sets of approaches such as parallelism, choices and sequential tasks. These event logs are used to test different approaches of discovering a configurable process model from a collection of event logs \cite{buijs2014flexible}.
  \item[Environmental Permit Application Process \cite{coselog-data}] This dataset originates from the "Configurable Services for Local Governments (CoSeLoG)" project \cite{van2011business} which investigates the similarities and dissimilarities between several processes of different municipalities in Netherlands. Dataset contains records of receiving phase for the building permit application process in 5 municipalities, which are comparable since activity labels in the different event logs refer to the same activities performed in five municipalities. This dataset is also mentioned in the literature as \textit{"Processing applications for building and/or environmental permits (Wet Algemene Bepalingen omgevingsrecht (WABO) in Dutch)"}.
\end{description}

### 2015-09-07 6_conclusion_future_work/conclusion_future_work.tex
no message

\section{Conclusion and Future Work}
\label{sec:conclusion-and-future-work}

\section{Conclusion}

In this study, a new approach is proposed and tested for generating recommendations using cross-organizational process mining for process performance improvement. Cross-organizational process mining is applied with the idea of unsupervised learning where predictor variables related to performances of organizations are used in an environment where processes are executed on several organizations. Results show that it is possible to use cross-organizational process mining and mismatch patterns for performance improvement recommendations. Process mining is a large-spectrum field where different set of activities and approaches are gathered together to discover, monitor and improve processes. In this  study, a four-stage solution is presented and their performances are explained. In addition, proposed methodology is developed as extensible and configurable set of plugins in ProM framework \cite{verbeek2010prom} and published as open-source. This makes the methodology open to include new process mining methods, mismatch patterns and clustering approaches as well as testing with different datasets.

\section{Future Work}

For the approach proposed in this thesis study, the following issues can be listed as pointers to future work:
\begin{itemize}
	\item In the process mining stage, instead of \textit{Inductive Miner}, different techniques can be used which can mine complex process models with higher appropriateness levels while keeping the current high fitness values.
	\item In the performance indicator analysis stage, new indicators can be defined based on the business environment, event log attributes and user needs. For instance, personnel and resource allocation indicators can be included as well as cost dimension.
	\item For mismatch pattern analysis, new and business oriented mismatch patterns can be included in the analysis. In addition analyzers can fail when there are loops in the process models in current implementations, therefore more robust implementations for process models with loops can be developed in the future.
	\item For the generated recommendations, their quality for business environment is not assessed within the scope of this thesis. However, when any feedback from a domain expert or BPM people is provided, the learning approach can be converted to semi-supervised learning from unsupervised learning.
\end{itemize}

### 2015-09-07 5_results_discussions/results_discussions.tex
no message

@@
 \end{description}
+
+%% datasets
+
+\section{Discussions}
+\label{sec:discussions}
+When the evaluation of the stages for \textit{Loan Application Process} and \textit{Environmental Permit Application Process} datasets are gathered together, the following results can be expressed:
+
+\begin{itemize}
+	\item Process mining stage of the proposed methodology can mine the process models with perfect fitness and high appropriateness from event logs which have no noise.
+When the noise level increases in the dataset, fitness values of mined models decreases to 90 \% levels with a decreasing appropriateness of models.
+	\item For the successfully mined models with high fitness values, replay and performance indicator calculation stage works seamlessly as expected.
+With this step, average and standard deviation time between each activity can be measured for each organization.
+Number of these metrics are quadratic to the number of activities in each organization's process model and difficult to analyze with a cross comparison.
+	\item Internal measure of clusters indicates that the organizations can be clustered according to their performance indicators which yields a collective approach of organizations for their subprocesses.
+In other words, within-SSE values decrease significantly when the organizations are divided into clusters which shows that they can be grouped based on how well they are executing in their performance indicators.
+	\item Mismatch analysis spots the differences between process models in coherence with structural similarity of them.
+This indicates that the idea of using mismatch patterns to reveal differences between process models is a feasible approach since its results are comparable to the similarity metrics of process models in the literature.
+	\item Recommendation generation aims to gather all generated information in this thesis study to help focusing on the potentially important mismatch patterns for performance improvement.
+For this aim, different thresholds and different cluster sizes are analyzed to check responsiveness of this stage.
+When the number of mismatch patterns with and without performance clusterings are checked, it shows that in a small dataset, where even the mismatch patterns can be spotted by visual analysis, performance clustering lists 3 times less number of differences in \textit{Loan Application Example} dataset.
+When it is impossible to locate mismatch patterns manually like in \textit{Environmental Permit Application Process}, performance clustering spots 100 times less number of differences.
+This difference helps user to focus on the differences with a potential performance improvement which is one of the aims in this thesis study.
+	\item Although each step of methodology can be counted as successful based on their evaluation metrics, mismatch patterns recommended at the end of methodology can yield important observations as well as being irrelevant and infeasible.
+Since this decision is based on the business environment of organizations, evaluation of the quality of recommendations for business usefulness requires domain expertise.
+However, an example recommendation can be presented to provide an insight.
+In the analysis of \textit{Environmental Permit Application Process} with 3 clusters, Cluster \#3 performs 40 \% better on average time and 53 \% better on standard deviation time between the activities "01\_HOOFD\_010" and "01\_HOOFD\_015".
+When the mismatch patterns between these clusters for the performance indicator is listed the following ones can be mentioned:
+		\begin{itemize}
+			\item Activity "03\_GBH\_005" and "16\_LGSV\_010"  are \textit{Different Moments in Processes} which have different next activities in clusters.
+			\item Activity "01\_HOOFD\_015"  and "01\_HOODF\_065" are \textit{Different Dependencies} patterns and they have a different set of dependencies in clusters.
+ 		\end{itemize}
+	Although the activity codes in mismatch patterns do not reveal any information about their context, they are listed as potential cause of performance improvement.
+For the municipality in Cluster \#3, the mentioned mismatch patterns are visualized on the fragments of process models in Figure~\ref{fig:coselog-wabo-recommendation-visualization-mun-3} since it is difficult to visualize the complete process models.
+In the process models, each mismatch pattern is marked and this shows how the proposed approach helps to focus on differences between process models.
+		\begin{figure}
+			\centering
+			\includegraphics[width=\textwidth]{5_results_discussions/coselog-wabo/recommendation-visualization-mun-3}
+			\caption{Visualization of example recommendation for Environmental Permit Application Process dataset (Municipality \#3)}
+		  \label{fig:coselog-wabo-recommendation-visualization-mun-3}
+		\end{figure}
+
+\end{itemize} % end of discussions

### 2015-09-07 5_results_discussions/coselog-wabo/coselog-wabo.tex
no message

\subsection{Environmental Permit Application Process}
\label{subsec:coselog-wabo-process}

### 2015-09-07 5_results_discussions/loan-application-process/loan-application-process.tex
no message

\subsection{Loan Application Process}
\label{subsec:loan-app-process}

In \textit{Loan Application Process} dataset there are a total of 475 cases and 2440 events with a fairly even distribution between variants and these variants are used as organizational logs and the methodology presented in this thesis study is be applied.

In \textit{Process Model Mining} stage, process models resulted with perfect fitness and high appropriateness as it is expected from a synthetically generated dataset without noise.

In \textit{Performance Indicator Analysis} stage, firstly event logs are replayed over process models and performance indicators are calculated and then organizations are clustered based on their performance indicators. In order to avoid overfitting,  with two clusters, Variant \#1, \#2, and \#4 are grouped into one cluster where only Variant \#3 is left to other cluster.

In \textit{Mismatch Pattern Analysis} stage, number of mismatch patterns are analyzed with the \textit{graph-edit similarity} between each two organization. As the similarity between process models decreases our method spots more mismatch patterns for most of the variants and it ensures that the developed mismatch pattern analyzers work as expected for this dataset.

In \textit{Recommendation Generation} stage, an organization and performance difference threshold is selected as analysis input. For the selected organization's cluster, all other clusters are checked for performing better than the specified threshold. Instead of all mismatch patterns between organizations, only the mismatch patterns that are potential causes of other organizations to perform better are listed. For different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:loan-recommendation-generation-analysis}. 
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{5_results_discussions/loan-application-process/recommendation-generation-analysis}
	\caption{Recommendation Generation analysis for Loan Application Process dataset}
  \label{fig:loan-recommendation-generation-analysis}
\end{figure}
In order to construct the data in Figure~\ref{fig:loan-recommendation-generation-analysis}, every organization is selected one-by-one with different threshold values. For every analysis, number of performance indicators and average number of mismatch patterns causing them are plotted. In addition, total number of mismatch patterns without clustering for each organization is added to the plot as an upper bound. With the help of this upper bound, responsiveness and degree of helping the user to focus on the performance improvement can be analyzed. As can be seen, for each threshold value, average number of mismatch patterns \textit{with performance indicator clustering} are very low compared to \textit{without clustering}. In other words, when user wants to improve its performance with any threshold, there is significantly less number of mismatch patterns on average to check. This shows the methodology proposed in this thesis can help users to focus on differences between organizations given this dataset.

### 2015-09-07 5_results_discussions/results_discussions.tex
no message

@@
 
-%% datasets
+\input{5_results_discussions/loan-application-process/loan-application-process.tex}
+\input{5_results_discussions/coselog-wabo/coselog-wabo.tex}
 
-\section{Discussions}
-\label{sec:discussions}
+\subsection{Discussions}
+\label{subsec:discussions}
 When the evaluation of the stages for \textit{Loan Application Process} and \textit{Environmental Permit Application Process} datasets are gathered together, the following results can be expressed:

### 2015-09-07 5_results_discussions/coselog-wabo/coselog-wabo.tex
no message

@@
 \label{subsec:coselog-wabo-process}
+
+In \textit{Environmental Permit Application Process} dataset \cite{coselog-data}, there are total of 1214 cases and 2142 events with a variable distribution between event logs of municipalities and municipalities are used as organizational logs.
+
+\begin{itemize}
+  \item In \textit{Process Model Mining} stage, with 10\% of noise threshold, high fitness values are achieved; however, some of the process models like Municipality \#5 and \#4 resulted with low appropriateness values.
+  \item In \textit{Performance Indicator Analysis} stage, after calculating the performance indicators, municipalities are clustered based on these values and three clusters are created, Municipality \#1 is located in the first cluster; Municipality \#2 and \#4 are located in the second cluster; and Municipality \#3 and \#5 are grouped in to the last cluster.
+  \item In \textit{Mismatch Pattern Analysis} stage, it can be stated that as the similarity between process models of municipalities increases, number of mismatch patterns decreases on most of the cases.
+When further analyzed, it can be seen that Municipalities \#4 and \#5, which have significantly more complex process model compared to others, fails in spotting mismatch patterns according to \textit{graph-edit similarity}.
+  \item In \textit{Recommendation Generation} stage, an organization and performance difference threshold is selected as analysis input likewise the previous dataset.
+For different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:coselog-wabo-recommendation-generation-analysis} for the thresholds of 25 \%, 50 \% and 75 \% since these are the breaking points for performance indicator changes.
+As plotted in Figure~\ref{fig:coselog-wabo-recommendation-generation-analysis-k3}, in addition to Municipality \#1, now Municipality \#3 and \#5 have the learning potential from other clusters.
+However, Municipality \#2 and \#4 performs better in all performance indicators which yielded no mismatch pattern analysis data for them.
+Increasing cluster sizes in this analysis shows that organizations can learn more from each other but it has the potential danger of overfitting to other organizations process model.
+	\begin{figure}
+		\centering
+		\includegraphics[width=\textwidth]{5_results_discussions/coselog-wabo/recommendation-generation-analysis-k3}
+		\caption{Recommendation Generation analysis for Environmental Permit Application Process dataset (3 Clusters)}
+	  \label{fig:coselog-wabo-recommendation-generation-analysis-k3}
+	\end{figure}
+\end{itemize}

### 2015-09-07 5_results_discussions/loan-application-process/loan-application-process.tex
no message

@@
 
-In \textit{Process Model Mining} stage, process models resulted with perfect fitness and high appropriateness as it is expected from a synthetically generated dataset without noise.
-
-In \textit{Performance Indicator Analysis} stage, firstly event logs are replayed over process models and performance indicators are calculated and then organizations are clustered based on their performance indicators.
+\begin{itemize}
+  \item In \textit{Process Model Mining} stage, process models resulted with perfect fitness and high appropriateness as it is expected from a synthetically generated dataset without noise.
+  \item In \textit{Performance Indicator Analysis} stage, firstly event logs are replayed over process models and performance indicators are calculated and then organizations are clustered based on their performance indicators.
 In order to avoid overfitting,  with two clusters, Variant \#1, \#2, and \#4 are grouped into one cluster where only Variant \#3 is left to other cluster.
-
-In \textit{Mismatch Pattern Analysis} stage, number of mismatch patterns are analyzed with the \textit{graph-edit similarity} between each two organization.
+  \item In \textit{Mismatch Pattern Analysis} stage, number of mismatch patterns are analyzed with the \textit{graph-edit similarity} between each two organization.
 As the similarity between process models decreases our method spots more mismatch patterns for most of the variants and it ensures that the developed mismatch pattern analyzers work as expected for this dataset.
-
-In \textit{Recommendation Generation} stage, an organization and performance difference threshold is selected as analysis input.
+  \item In \textit{Recommendation Generation} stage, an organization and performance difference threshold is selected as analysis input.
 For the selected organization's cluster, all other clusters are checked for performing better than the specified threshold.
@@
 This shows the methodology proposed in this thesis can help users to focus on differences between organizations given this dataset.
+\end{itemize}

### 2015-09-08 1_introduction/introduction.tex
no message

@@
 Traditional process mining approaches work on a single organization; however, with the increase of cloud computing and shared infrastructures, event logs of multiple organizations are currently available for analysis where cross-organizational process mining stands out.
-In cross-organizational process mining area, recent studies focus on commonality and collaboration between organizations.
-Studies focus on how similar the process models and behaviors of organizations under cross comparison \cite{buijs2012towards} and challenges based on partitioning of tasks and process models between organizations \cite{van2011intra}.
+In cross-organizational process mining area, recent studies focus on commonality and collaboration between organizations, especially on how similar the process models and behaviors of organizations under cross comparison \cite{buijs2012towards} and challenges based on partitioning of tasks and process models between organizations \cite{van2011intra}.
 This study is based on the environment where processes are executed on several organizations and cross-organizational process mining is applied with the idea of unsupervised learning where predictor variables related to performances of organizations are used.

### 2015-09-08 2_relatedwork/relatedwork.tex
no message

--- 2015-08-31 2_relatedwork/relatedwork.tex
@@
 
-In this section, studies related to the work presented in this thesis are summarized.
+In this section, studies related to the work presented in this research are summarized.
 Firstly, studies in the process mining area are explained and then studies from cross-organizational process mining, which is the main topic of this research, is introduced.
-Following these, studies related to similarity in process mining is mentioned.
-Finally, performance and conformance analysis approaches in process mining area are presented.
+Following these, studies related to similarity in process mining are presented.
 
 Within the process mining framework, there are various different process mining algorithms proposed which have the same aim of discovering underlying processes.
-Considering the underlying approaches undertaken, algorithms can be grouped as $\alpha$-algorithms \cite{van2004workflow,de2004process}, inductive approaches \cite{herbst1998integrating,herbst2000dealing}, hierarchical clustering \cite{greco2005mining}, genetic approaches \cite{van2005genetic,esgin2010hybrid}, and heuristic approaches \cite{esgin2009hybrid}.
+Considering the underlying approaches, algorithms can be grouped as $\alpha$-algorithms \cite{van2004workflow,de2004process}, inductive approaches \cite{herbst1998integrating,herbst2000dealing}, hierarchical clustering \cite{greco2005mining}, genetic approaches \cite{van2005genetic,esgin2010hybrid}, and heuristic approaches \cite{esgin2009hybrid}.
 Considering the scope of this study; process discovery operations are undertaken with inductive methods which is a robust, repeatable and mature set of approaches.
+
+Cross-organizational mining is based on cross-correlation of workflows and the realized activities in different organization to compare in an objective approach.
+In the study of Bujis et al.
+\cite{buijs2012towards}, process models and behaviors of organizations are cross-compared with the idea of supporting and representing.
+In the studies of van der Aalst \cite{van2011business,van2011intra}, configurable process models are proposed with the ideas of \textit{exploiting commonality} and \textit{collaboration} for the organizations sharing the same infrastructure and doing the similar work.
+In this study, usage of cross-organizational process mining is based on \textit{exploiting commonality} where organizations can learn from each other.
+
+Similarity in process mining have various approaches which focus on metrics \cite{dijkman2011similarity}, analytical comparison \cite{buijs2014comparing}, delta analysis \cite{esgin2011delta,esgin2013sequence} and mismatch patterns \cite{dijkman2007mismatch}.
+In this research, combination of metric and mismatch pattern approaches are used to identify variations between process models of different organizations that execute the same tasks.

### 2015-09-08 3_background/background.tex
no message

@@
 
-In this section background information is presented for the relevant topics to this thesis study.
-Process discovery approaches and then mismatch patterns in process models are presented.
-All topics in this chapter are limited to the scope of this thesis study with the aim of constructing a necessary background.
+In this section process discovery methods and mismatch patterns are presented within the  the scope of this resarch thesis and the aim of constructing a necessary background.
 
-In process mining field, one of the most challenging tasks is to construct a process model based on the behavior in the event logs, namely process discovery.
-Many process discovery algorithms are proposed to address different challenges in process discovery and using different notations.
+In process mining field, various process discovery algorithms are proposed to address different challenges in process discovery and using different notations.
 However, in this study focus of the study is learning from the cross-organizational process mining rather than addressing all process discovery challenges.
@@
 In order to align these processes and organizations, there is a need for spotting differences between process models.
-In the study of Dijkman \cite{dijkman2007mismatch}, a collection of patterns to describe frequent mismatches between the similar process models are presented.Within the scope of this study, the related mismatch patterns are defined in study \cite{dijkman2007mismatch} as follows:
+In the study of Dijkman \cite{dijkman2007mismatch}, a collection of patterns to describe frequent mismatches between the similar process models are presented.
+Within the scope of this study, the related mismatch patterns are defined in study \cite{dijkman2007mismatch} as follows:
 \begin{description}

### 2015-09-08 4_methodology/methodology.tex
no message

@@
 Then, each stage in the methodology is presented together with their importance in the study, mathematical representations and definitions; and black-box diagrams.
-In the last section of this chapter, implementation details of this methodology in ProM framework is explained in detail with a software architecture overview.
+Finally, implementation details of this methodology in ProM framework is explained in detail with a software architecture overview.
 
@@
 Finally, in \textit{Recommendation Generation}, using the performance indicator clusterings and differences between process models, a set of recommendations for each organization is generated.
-In the following sections, each stage will be explained in detail with their mathematical backgrounds.
-
 \begin{figure}
@@
 In order to achieve this aim, implementation of \textit{Inductive Miner Infrequent (IMi)}, which is proposed in \cite{leemans2014discoveringinfrequent} as an extension to \textit{Inductive Miner} to handle noise in the event logs, is used in this study.
-Considering the scope of this study, instead of computational details of \textit{Inductive Miner Infrequent (IMi)}; black-box representation is used to explain its usage in the methodology.
 In order to set a filtering threshold, a user-provided value between 0 to 1 is added as input to method in addition to event logs.
-As a result, workflow net is produced which is a sound and properly completed Petri net without deadlocks.
 Black-box of this stage is illustrated in Figure~\ref{fig:process-model-mining-blackbox} and this stage is called for every organization's event logs to create their own process models in Workflow net formalization.
-
 \begin{figure}
@@
 Replay of event logs on process models is based on the idea of \textit{alignment} which is formalized in \cite{van2012replaying} and the basic assumption in this concept is that process models and event logs have the same activity labels.
-Alignment is based on \textit{moves in the model and log} and in order to have a successful replay where optimal alignment should be achieved.
-As proposed in \cite{adriansyah2011conformance,adriansyah2011towards}, $A^{*}$ algorithm which is a path-finding algorithm based on graphs is used to find optimal alignment of event logs on the process models.
-With the generated and user-specified inputs, replay and performance indicator calculation in the methodology can be visualized in Figure~\ref{fig:replay-and-performance-indicator-calculation}.
-For each organization, the steps in the diagram are followed with the corresponding event logs and process models; and the resulting process summaries are used for further analysis.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{4_methodology/replay-and-performance-indicator-calculation}
-  \caption{Replay and Performance Indicator Calculation Stage as Black-box}
-  \label{fig:replay-and-performance-indicator-calculation}
-\end{figure}
+For each organization, the steps alignment and creating transitions are undertaken with the corresponding event logs and process models; and the resulting process summaries are used for further analysis.
 
@@
 \label{subsubsec:performance-indicator-clustering}
-
 Clustering is based on the idea of collecting the set of observations into clusters so that observations within the same cluster are similar whereas the observations from different clusters are dissimilar.
-In this thesis study, clustering is used to gather organizations based on their performance indicator data.
-In this study, a generic approach based on centroid-based clustering is exploited.
-For the fixed number of \textit{k} clusters, the approach is well-known as \textit{k-means clustering}.
-Considering the popularity of this approach and its extensions, random initialization based \textit{k-means++} approach from the study of Arthur and Vassilvitskii \cite{arthur2007} is used to cluster organizations.
-For each organization, \textit{Performance Summary} data is used as the data source in clustering.
+In this study, clustering is used to gather organizations based on their performance indicator data.
+In this research, random initialization based \textit{k-means++} approach from the study of Arthur and Vassilvitskii \cite{arthur2007} is used to cluster organizations.
 Since number of clusters are not known priori, k-means clustering is applied starting \textit{k} from 1 to the number of organizations.
@@
 In the process mining stage, process models are mined to create Workflow nets; however, mismatch pattern definitions are closer to business environment and it is more suitable spot patterns in BPMN notation.
-Thus, mined process models are converted to BPMN models and then mismatch pattern analysis is applied.
-After spotting differences, mismatch patterns for activities and control flows are revealed for the organizations.
-
-Business Process Modeling Notation (BPMN) is one of the widely accepted modeling language in the industry and its a standardized notation by the Object Management Group (OMG) since 2004.
-In this stage, BPMN formulation is used since mismatch patterns have roots in real-life business environment \cite{dijkman2007mismatch}.
-
-For each organization, mined process models are converted to BPMN models and mismatch patterns analysis is undertaken on them, in order to locate differences between two process models or cluster of process models.
+Thus, mined process models are converted to BPMN models and then mismatch pattern analysis is applied in order to locate differences between two process models or cluster of process models.
 In addition, since performance indicators are calculated based on a starting and ending points in the process model, same approach is applied to locate mismatch patterns.
 In other words, differences of process models are located through a starting activity to an ending activity.
-When the complete set of mismatches between process models are required, this approach is used with starting and ending points as source and sink activities.
 For each organization, mismatch patterns are gathered and stored for the further analysis as visualized in Figure~\ref{fig:mismatch-pattern-analysis-blackbox}.
-
 \begin{figure}
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{4_methodology/recommendation-generation-blackbox}
+  \includegraphics[width=0.5\textwidth]{4_methodology/recommendation-generation-blackbox}
   \caption{Recommendation Generation Stage as Black-box}
@@
 \label{subsec:implementation}
-Methodology of this thesis study is implemented in ProM \cite{verbeek2010prom}, which is an extensible framework that supports a wide variety of process mining techniques in form of plugins.
-ProM is an open source framework for process mining algorithms which provides a platform to users and developers.
-Aim of this framework is to create a standard process mining platform that is accepted in industry and academia with an active community.
-Approach of this thesis study is implemented with its each stage as a standalone plugin that enables extensions for further studies.
+Methodology of this study is implemented in ProM \cite{verbeek2010prom}, which is an extensible framework that supports a wide variety of process mining techniques in form of plugins.
+Approach of this study is implemented with its each stage as a standalone plugin that enables extensions for further studies.
 Developed set of plugins are packaged with the name of \textit{CrossOrgProcMin}\footnote{\url{http://www.promtools.org/prom6/packages/CrossOrgProcMin}} and published open-source\footnote{\url{http://github.com/onuryilmaz/cross-org-proc-min}} being available in the latest version of ProM release.
-
-Approach of this study is divided into stand-alone stages where inputs and outputs between them are defined strictly.
-With the help of this understanding, each stage is developed as a stand-alone plug-in in ProM framework which can be called separately.
-For this aim, five plug-ins are developed which are visualized in Figure~\ref{fig:architecture} to provide a high-level perspective.
-In addition, a set of utilities are developed to visualize and persistence of data in ProM environment.
-\begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{4_methodology/architecture}
-  \caption{Software Architecture for  Cross-Organizational Process Miner}
-  \label{fig:architecture}
-\end{figure}

### 2015-09-08 5_results_discussions/coselog-wabo/coselog-wabo.tex
no message

--- 2015-09-07 5_results_discussions/coselog-wabo/coselog-wabo.tex
@@
 \label{subsec:coselog-wabo-process}
+\textit{Environmental Permit Application Process} dataset originates from the "Configurable Services for Local Governments (CoSeLoG)" project \cite{van2011business} which investigates the similarities and dissimilarities between several processes of different municipalities in Netherlands.
+Dataset contains records of receiving phase for the building permit application process in 5 municipalities, which are comparable since activity labels in the different event logs refer to the same activities performed in five municipalities.
+In this dataset \cite{coselog-data}, there are total of 1214 cases and 2142 events with a variable distribution between event logs of municipalities and municipalities are used as organizational logs.
+
+\begin{itemize}
+  \item In \textit{Process Model Mining} stage, with 10\% of noise threshold, high fitness values are achieved; however, some of the process models like Municipality \#4 and \#5 resulted with low appropriateness values.
+  \item In \textit{Performance Indicator Analysis} stage, after calculating the performance indicators, municipalities are clustered and three clusters are created: Municipality \#1 is located in the first cluster; Municipality \#2 and \#4 are located in the second cluster; and Municipality \#3 and \#5 are grouped in to the last cluster.
+  \item In \textit{Mismatch Pattern Analysis} stage, it can be stated that as the similarity between process models of municipalities increases, number of mismatch patterns decreases on most of the cases.
+When further analyzed, it can be seen that Municipalities \#4 and \#5, which have significantly more complex process model compared to others, fails in spotting mismatch patterns according to \textit{graph-edit similarity}.
+  \item In \textit{Recommendation Generation} stage, for different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:coselog-wabo-recommendation-generation-analysis} for the thresholds of 25 \%, 50 \% and 75 \% since these are the breaking points.
+For instance, cluster of Municipality \#1 performs worse in 6 indicators with the difference of 25 \% and on average 5 mismatch patterns are listed for each performance indicator.
+When it is compared to the total mismatch patterns of Municipality #1, which is 357, proposed approach helps significantly to the user for focusing performance improvement.
+	\begin{figure}
+		\centering
+		\includegraphics[width=\textwidth]{5_results_discussions/coselog-wabo/recommendation-generation-analysis-k3}
+		\caption{Recommendation Generation analysis for Environmental Permit Application Process dataset (3 Clusters)}
+	  \label{fig:coselog-wabo-recommendation-generation-analysis-k3}
+	\end{figure}
+\end{itemize}

### 2015-09-08 5_results_discussions/loan-application-process/loan-application-process.tex
no message

@@
 \label{subsec:loan-app-process}
-
-In \textit{Loan Application Process} dataset there are a total of 475 cases and 2440 events with a fairly even distribution between variants and these variants are used as organizational logs and the methodology presented in this thesis study is be applied.
+\textit{Loan Application Process} dataset is synthetically created and consists of four variants of a simple loan application in a financial institute.
+These event logs are used to test different approaches of discovering a configurable process model from a collection of event logs \cite{buijs2014flexible}.
+In this dataset there are a total of 475 cases and 2440 events with a fairly even distribution between variants and these variants are used as organizational logs and the methodology presented in this thesis study is be applied.
 
@@
   \item In \textit{Mismatch Pattern Analysis} stage, number of mismatch patterns are analyzed with the \textit{graph-edit similarity} between each two organization.
-As the similarity between process models decreases our method spots more mismatch patterns for most of the variants and it ensures that the developed mismatch pattern analyzers work as expected for this dataset.
-  \item In \textit{Recommendation Generation} stage, an organization and performance difference threshold is selected as analysis input.
-For the selected organization's cluster, all other clusters are checked for performing better than the specified threshold.
-Instead of all mismatch patterns between organizations, only the mismatch patterns that are potential causes of other organizations to perform better are listed.
-For different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:loan-recommendation-generation-analysis}.
+As the similarity between process models decreases our method spots more mismatch patterns and it ensures that the developed mismatch pattern analyzers work as expected for this dataset.
+  \item In \textit{Recommendation Generation} stage, for different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:loan-recommendation-generation-analysis}.
     \begin{figure}
@@
   In order to construct the data in Figure~\ref{fig:loan-recommendation-generation-analysis}, every organization is selected one-by-one with different threshold values.
-For every analysis, number of performance indicators and average number of mismatch patterns causing them are plotted.
-In addition, total number of mismatch patterns without clustering for each organization is added to the plot as an upper bound.
+For each analysis, number of performance indicators and average number of mismatch patterns causing them are plotted.
+In addition, total number of mismatch patterns without clustering is added as an upper bound.
 With the help of this upper bound, responsiveness and degree of helping the user to focus on the performance improvement can be analyzed.
@@
 In other words, when user wants to improve its performance with any threshold, there is significantly less number of mismatch patterns on average to check.
-This shows the methodology proposed in this thesis can help users to focus on differences between organizations given this dataset.
+This shows the methodology proposed in this study can help users to focus on differences between organizations given this dataset.
 \end{itemize}

### 2015-09-08 5_results_discussions/results_discussions.tex
no message

--- 2015-09-07 5_results_discussions/results_discussions.tex
@@
 Approach in this study is an aggregation of various methods and they are significantly different from each other in their mathematical background.
-Therefore, instead of a global evaluation metric for the complete methodology, each stage will be evaluated within its evaluation metrics.
-Since these stages are executed sequentially, it is important for each stage to perform well enough to yield a successful outcome.
-Evaluation metrics for each stage are as follows:
-
+Therefore, instead of a global evaluation metric for the complete methodology, each stage is evaluated within its evaluation metrics which are as follows:
 \begin{description}
-	\item[Process Model Mining] Performance of process mining stage is measured by \textit{Fitness} and \textit{Appropriateness} which are defined in \cite{rozinat2008conformance}.
+	\item[Process Model Mining] Performance of process mining stage is measured by \textit{fitness} and \textit{appropriateness} which are defined in \cite{rozinat2008conformance}.
 	\item[Performance Indicator Analysis] In replay phase, \textit{alignment costs} \cite{van2012replaying} are compared with process model mining metrics.
-In clustering phase, within-SSE analysis is undertaken to decide on the number of clusters.
+In clustering phase, \textit{within-SSE} analysis is undertaken to decide on the number of clusters.
 	\item[Mismatch Pattern Analysis] In this stage, number of mismatch patterns found are compared with the \textit{graph-edit similarity} \cite{dijkman2011similarity} of process models.
@@
 
-Cross-organizational mining aims to find cross-correlation of workflows and activities in different organizations and this yields the necessity of organizations that do the same main activity with comparable process flows.
-Considering these characteristics, there are few dataset available in the literature that are well-structured, documented and valuable.
-In this thesis study, one synthetic and one real-life event log datasets are presented and used in the following sections to evaluate the performance of the proposed methodology.
+\input{5_results_discussions/loan-application-process/loan-application-process.tex}
+\input{5_results_discussions/coselog-wabo/coselog-wabo.tex}
 
-\begin{description}
-  \item[Loan Application Process \cite{loan-app-data}] This synthetically created dataset consists of event log variants of a simple loan application in a financial institute.
-This dataset includes artificial event logs of 4 variants where each variant includes different sets of approaches such as parallelism, choices and sequential tasks.
-These event logs are used to test different approaches of discovering a configurable process model from a collection of event logs \cite{buijs2014flexible}.
-  \item[Environmental Permit Application Process \cite{coselog-data}] This dataset originates from the "Configurable Services for Local Governments (CoSeLoG)" project \cite{van2011business} which investigates the similarities and dissimilarities between several processes of different municipalities in Netherlands.
-Dataset contains records of receiving phase for the building permit application process in 5 municipalities, which are comparable since activity labels in the different event logs refer to the same activities performed in five municipalities.
-This dataset is also mentioned in the literature as \textit{"Processing applications for building and/or environmental permits (Wet Algemene Bepalingen omgevingsrecht (WABO) in Dutch)"}.
-\end{description}
+\subsection{Discussions}
+\label{subsec:discussions}
+When the evaluation of the stages for \textit{Loan Application Process} and \textit{Environmental Permit Application Process} datasets are gathered together, the following results can be expressed:
+
+\begin{itemize}
+	\item Process mining stage of the proposed methodology can mine the process models with high fitness appropriateness levels.
+	\item For the successfully mined models with high fitness values, replay and performance indicator calculation stage works seamlessly as expected.
+With this step, average and standard deviation time between each activity can be measured for each organization.
+Number of these metrics are quadratic to the number of activities in each organization's process model and difficult to analyze with a cross comparison.
+	\item Internal measure of clusters indicates that the organizations can be clustered according to their performance indicators which yields a collective approach of organizations for their subprocesses.
+In other words, organizations are divided into clusters which shows that they can be grouped based on how well they are executing.
+	\item Mismatch analysis spots the differences between process models in coherence with structural similarity of them.
+This indicates that the idea of using mismatch patterns to reveal differences between process models is a feasible approach since its results are comparable to the similarity metrics of process models in the literature.
+	\item Recommendation generation aims to gather all generated information in this study to help focusing on the potentially important mismatch patterns for performance improvement.
+When the number of mismatch patterns with and without performance clusterings are checked, it shows that in a small dataset performance clustering lists 3 times less number of differences in \textit{Loan Application Example} dataset.
+When it is impossible to locate mismatch patterns manually like in \textit{Environmental Permit Application Process}, performance clustering spots 100 times less number of differences.
+This difference helps user to focus on the differences with a potential performance improvement which is one of the aims in this thesis study.
+	\item Although each step of methodology can be counted as successful based on their evaluation metrics, mismatch patterns recommended at the end of methodology can yield important observations as well as being irrelevant and infeasible.
+Since this decision is based on the business environment of organizations, evaluation of the quality of recommendations for business usefulness requires domain expertise.
+However, an example recommendation can be presented to provide an insight.
+In the analysis of \textit{Loan Application Process}, Variant \#3 performs worse 27 \%  on average time and 12 \% on standard deviation time between activities "Calculate Capacity" and "Accept".
+When the mismatch patterns for these performance indicators are checked the following ones can be mentioned:
+		\begin{itemize}
+		\item "Check Credit" is a \textit{Refined Activity} of with "Check System (50 \%)"; "Check Paper Archive (42 \%)"; "Send Credit Check Request (32 \%)"; "Process Credit Check Reply (31 \%)" where the corresponding similarity values provided in parentheses.
+		\item "Calculate Capacity" is a \textit{Different Moments in Processes} which have different previous activities in clusters. 
+		\end{itemize}
+	When these example mismatch patterns are checked, removing "Check Credit" activity and putting other activities instead of it might be the cause of performance improvement.
+With the same approach, putting "Calculate Capacity" on different orders in processes can effect the average and variance of time between activities.
+These mismatch patterns are also visualized on process model of Variant \#3 and a variant from other cluster in Figure~\ref{fig:loan-recommendation-visualization}.
+In the process models, refined activities of "Check Credit" and different positions of "Calculate Capacity" are indicated.
+		\begin{figure}
+			\centering
+			\includegraphics[width=\textwidth]{5_results_discussions/loan-application-process/recommendation-visualization}
+			\caption{Visualization of example recommendation for Loan Application Process dataset}
+		  \label{fig:loan-recommendation-visualization}
+		\end{figure}
+\end{itemize} % end of discussions

### 2015-09-08 6_conclusion_future_work/conclusion_future_work.tex
no message

@@
 \label{sec:conclusion-and-future-work}
-
-\section{Conclusion}
 
@@
 Results show that it is possible to use cross-organizational process mining and mismatch patterns for performance improvement recommendations.
-Process mining is a large-spectrum field where different set of activities and approaches are gathered together to discover, monitor and improve processes.
 In this study, a four-stage solution is presented and their performances are explained.
@@
 
-\section{Future Work}
-
-For the approach proposed in this thesis study, the following issues can be listed as pointers to future work:
+For the approach proposed in this study, the following issues can be listed as pointers to future work:
 \begin{itemize}
@@
 In addition analyzers can fail when there are loops in the process models in current implementations, therefore more robust implementations for process models with loops can be developed in the future.
-	\item For the generated recommendations, their quality for business environment is not assessed within the scope of this thesis.
+	\item For the generated recommendations, quality for business environment is not assessed within the scope of this study.
 However, when any feedback from a domain expert or BPM people is provided, the learning approach can be converted to semi-supervised learning from unsupervised learning.

### 2015-09-08 3_background/background.tex
no message

@@
 
-In this section process discovery methods and mismatch patterns are presented within the  the scope of this resarch thesis and the aim of constructing a necessary background.
+In this section process discovery methods and mismatch patterns are presented within the  the scope of this resarch and the aim of constructing a necessary background.
 

### 2015-09-08 5_results_discussions/loan-application-process/loan-application-process.tex
no message

@@
 These event logs are used to test different approaches of discovering a configurable process model from a collection of event logs \cite{buijs2014flexible}.
-In this dataset there are a total of 475 cases and 2440 events with a fairly even distribution between variants and these variants are used as organizational logs and the methodology presented in this thesis study is be applied.
+In this dataset there are a total of 475 cases and 2440 events with a fairly even distribution between variants and these variants are used as organizational logs and the methodology presented in this study is be applied.
 

### 2015-09-08 1_introduction/introduction.tex
no message

@@
 
-The rest of the paper is organized as follows:
-\begin{inparaenum}
-	\item In Section~\ref{sec:relatedwork}, related studies in process mining area are presented. 
-	\item In Section~\ref{sec:background}, background information for the relevant topics is explained.
-	\item In Section~\ref{sec:methodology}, methodology proposed in this study is presented with detail.
-	\item In Section~\ref{sec:results-and-discussions}, methodology of this study is applied on datasets and results are discussed.
-	\item In Section~\ref{sec:conclusion-and-future-work}, summary of this study is presented with the final remarks and pointers for future work. 
-\end{inparaenum}
+The rest of the paper is organized as follows: In Section~\ref{sec:relatedwork}, related studies in process mining area are presented.
+In Section~\ref{sec:background}, background information for the relevant topics is explained.
+In Section~\ref{sec:methodology}, methodology proposed in this study is presented with detail.
+In Section~\ref{sec:results-and-discussions}, methodology of this study is applied on datasets and results are discussed.
+In Section~\ref{sec:conclusion-and-future-work}, summary of this study is presented with the final remarks and pointers for future work.

### 2015-09-15 1_introduction/introduction.tex
no message

@@
 The approach proposed in this study is a four-stage solution and it starts with mining the process models of organizations; followed by performance indicator analysis and then mismatch pattern analysis.
-Finally recommendation generation stage is undertaken to create learning opportunities for each organization.
+Finally in the suggestion generation stage, learning opportunities are created for each organization.
 With this approach it is aimed to help business process management users to focus on the potentially important parts of their business maps.
 Proposed methodology is implemented in ProM framework \cite{verbeek2010prom} as a set of plugins corresponding for each stage and packaged under the name of \textit{CrossOrgProcMin} and tested on a synthetic and real-life event logs.
-Performance of methodology is assessed with a defined evaluation metrics for each stage and resulting recommendations are presented to show how this approach helps users to focus on learning opportunities between organizations with a performance improvement potential.
+Performance of methodology is assessed with a set of defined evaluation metrics for each stage and resulting recommendations are presented to show how this approach helps users to focus on learning opportunities between organizations with a performance improvement potential.
 

### 2015-09-15 2_relatedwork/relatedwork.tex
no message

@@
 
-In this section, studies related to the work presented in this research are summarized.
-Firstly, studies in the process mining area are explained and then studies from cross-organizational process mining, which is the main topic of this research, is introduced.
+In this section, studies related to the presented work are summarized.
+Firstly, studies in the process mining area are explained and then studies from cross-organizational process mining, which is the main topic of this research, are introduced.
 Following these, studies related to similarity in process mining are presented.

### 2015-09-15 3_background/background.tex
no message

@@
 
-In this section process discovery methods and mismatch patterns are presented within the  the scope of this resarch and the aim of constructing a necessary background.
-
+In this section, process discovery methods and mismatch patterns are presented within the scope of this work.
 In process mining field, various process discovery algorithms are proposed to address different challenges in process discovery and using different notations.
-However, in this study focus of the study is learning from the cross-organizational process mining rather than addressing all process discovery challenges.
-With this reasoning, Inductive Process Mining \cite{leemans2013discovering} is selected as appropriate since it is simple, highly applicable and configurable.
+In this study, since the focus is learning lessons from cross-organizational mining, we used Inductive Process Mining \cite{leemans2013discovering} for process discovery, which is simple, highly applicable and configurable.
 In the literature, its derivatives which handles infrequent behaviors \cite{leemans2014discoveringinfrequent}; incomplete logs \cite{leemans2014discoveringincomplete}; and model optimization \cite{weidlich2012profiles} are also available.
@@
 
-In cross-organizational process mining environment, there is a need to align processes of different organizations and in this scope both the organizations and their processes are similar but have significant differences.
-In order to align these processes and organizations, there is a need for spotting differences between process models.
+In cross-organizational process mining environment, there is a need to align processes of different organizations.
+In order to align these processes and organizations, a mechanism is needed for spotting differences between process models.
 In the study of Dijkman \cite{dijkman2007mismatch}, a collection of patterns to describe frequent mismatches between the similar process models are presented.
@@
 
-As mentioned in the study \cite{dijkman2007mismatch}, their approach does not create a comprehensive list to resolve all mismatches but the most common ones spotted during case studies.
+As mentioned in the study \cite{dijkman2007mismatch}, their approach does not create a comprehensive list to resolve all mismatches but includes the most common mismatch patterns spotted during case studies.
 In addition, from their definitions and examples it can be easily seen that these patterns are not orthogonal.
-Moreover, there are no algorithms provided to spot these mismatches in \cite{dijkman2007mismatch} or consequent studies, and thus implementation of spotting mismatch patterns are kept within the scope of this study.
+Moreover, there are no algorithms provided to spot these mismatches in \cite{dijkman2007mismatch} or consequent studies, and thus implementation of spotting mismatch patterns are performed within the scope of this study.

### 2015-09-15 4_methodology/methodology.tex
no message

@@
 In order to achieve this aim, implementation of \textit{Inductive Miner Infrequent (IMi)}, which is proposed in \cite{leemans2014discoveringinfrequent} as an extension to \textit{Inductive Miner} to handle noise in the event logs, is used in this study.
-In order to set a filtering threshold, a user-provided value between 0 to 1 is added as input to method in addition to event logs.
+In order to set a filtering threshold, a user-provided value between 0 to 1 is added as input to the method in addition to event logs.
 Black-box of this stage is illustrated in Figure~\ref{fig:process-model-mining-blackbox} and this stage is called for every organization's event logs to create their own process models in Workflow net formalization.
@@
 \label{subsec:performance-indicator-analysis}
-Performance indicator analysis stage focuses on calculating and analyzing the performance values using the event logs and mined process models. This stage consists of mainly two concepts as 
+Performance indicator analysis stage focuses on calculating and analyzing the performance values using the event logs and mined process models. This stage consists of mainly two steps as 
 \begin{inparaenum}[\itshape a\upshape)]
@@
 However, in this study, process related performance values are considered since differences in the process models are studied in the next stages.
-With this reasoning, the following performance indicators are calculated and analyzed in this stage of methodology:
+To this aim, the following performance indicators are calculated and analyzed in this stage of methodology:
 \begin{description}
-	\item[Average Time Between Activities] For each activity in the process model, average time to reach other activity is calculated.
+	\item[Average Time Between Activities] For each activity in the process model, average time to reach the next activity is calculated.
 This is a simple but powerful performance metric for organizations since it can yield the average time to complete one task based on a starting point.
 From the performance perspective, organizations want to minimize average time between activities to increase their throughput \cite{van2012replaying}.
-	\item[Standard Deviation of Time Between Activities] Time between activities in real life is not stable and they deviate due to various reasons such as people responsible of tasks, size and the content of tasks or seasonality \cite{van2011process}.
+	\item[Standard Deviation of Time Between Activities] Time between activities in real life is not stable and they deviate due to various reasons such as the user responsible of tasks, size and the content of tasks or seasonality \cite{van2011process}.
 On the other hand, organizations want to be confident about their processes and therefore they want to minimize the deviation in the time between activities.
@@
 Replay of event logs on process models is based on the idea of \textit{alignment} which is formalized in \cite{van2012replaying} and the basic assumption in this concept is that process models and event logs have the same activity labels.
-For each organization, the steps alignment and creating transitions are undertaken with the corresponding event logs and process models; and the resulting process summaries are used for further analysis.
+For each organization, the steps of alignment and creating transitions are performed with the corresponding event logs and process models; and the resulting process summaries are used for further analysis.
 
@@
 In this research, random initialization based \textit{k-means++} approach from the study of Arthur and Vassilvitskii \cite{arthur2007} is used to cluster organizations.
-Since number of clusters are not known priori, k-means clustering is applied starting \textit{k} from 1 to the number of organizations.
-For each clustering with different number of clusters, SSE values are plotted and user is made to select the appropriate cluster size.
+Since the number of clusters are not known priori, k-means clustering is applied starting \textit{k} from 1 to the number of organizations.
+For each clustering with different number of clusters, SSE values are plotted and user is asked to select the appropriate cluster size.
 For the selected cluster size, clustering related information is used to generate recommendations in the further steps.
@@
 In order to learn from other organizations, it is necessary to spot the differences between process models of different organizations.
-In this phase of methodology, differences between process models will be revealed by the mismatch patterns which are defined by Dijkman \cite{dijkman2007mismatch}.
+In this phase, differences between process models will be revealed by the mismatch patterns which are defined by Dijkman \cite{dijkman2007mismatch}.
 In the process mining stage, process models are mined to create Workflow nets; however, mismatch pattern definitions are closer to business environment and it is more suitable spot patterns in BPMN notation.
-Thus, mined process models are converted to BPMN models and then mismatch pattern analysis is applied in order to locate differences between two process models or cluster of process models.
-In addition, since performance indicators are calculated based on a starting and ending points in the process model, same approach is applied to locate mismatch patterns.
+Thus, mined process models are converted to BPMN models and then mismatch pattern analysis is applied in order to locate the differences between two process models or two clusters of process models.
+In addition, since performance indicators are calculated based on a starting and ending point in the process model, the same approach is applied to locate mismatch patterns.
 In other words, differences of process models are located through a starting activity to an ending activity.
@@
 In this study, idea of recommendation is based on providing a set of mismatch patterns for each organization so that they can enhance their processes.
-These mismatch patterns are generated by comparing the process models of other organizations, particularly which are performing better in terms of their performance indicator values.
+These mismatch patterns are generated by comparing the process models of other organizations, particularly those that are performing better in terms of their performance indicator values.
 In addition, clustering of organizations is undertaken to generalize the way of identifying which organizations perform better in this environment.
@@
 After finding significant difference, all organizations in other clusters are checked against mismatch patterns with the starting and ending activities defined in performance indicators.
-With this constraining, only mismatches which are located between the activities that causes high level of difference in performance indicators are analyzed.
+Only mismatches which are located between the activities that causes high level of difference in performance indicators are analyzed.
 
@@
 In addition, a performance difference threshold is gathered from the user to specify how much difference between clusters is necessary to check for mismatch patterns and generate recommendations.
-This stage generates recommendation data for each organization which contains a set of mismatch patterns.
+This stage generates recommendation data for each organization that contains a set of mismatch patterns.
 \begin{figure}

### 2015-09-15 5_results_discussions/loan-application-process/loan-application-process.tex
no message

@@
 \textit{Loan Application Process} dataset is synthetically created and consists of four variants of a simple loan application in a financial institute.
-These event logs are used to test different approaches of discovering a configurable process model from a collection of event logs \cite{buijs2014flexible}.
+These event logs are used for testing different approaches of discovering a configurable process model from a collection of event logs \cite{buijs2014flexible}.
 In this dataset there are a total of 475 cases and 2440 events with a fairly even distribution between variants and these variants are used as organizational logs and the methodology presented in this study is be applied.

### 2015-09-15 5_results_discussions/results_discussions.tex
no message

@@
 
-In this section, methodology presented in this study is applied on datasets and results are presented.
+In this section, methodology presented in this study is applied on several data sets and results are presented.
 Firstly, evaluation metrics are defined for each stage of methodology to assess the performance of approach.
-Following this, methodology is applied on two datasets and results are explained with discussions.
+Following this, methodology is applied on two data sets and results are explained with discussions.
 
@@
 When it is impossible to locate mismatch patterns manually like in \textit{Environmental Permit Application Process}, performance clustering spots 100 times less number of differences.
-This difference helps user to focus on the differences with a potential performance improvement which is one of the aims in this thesis study.
+This difference helps user to focus on the differences with a potential performance improvement which is one of the aims in this study.
 	\item Although each step of methodology can be counted as successful based on their evaluation metrics, mismatch patterns recommended at the end of methodology can yield important observations as well as being irrelevant and infeasible.

### 2015-09-15 paper.tex
no message

@@
 \usepackage[math]{blindtext}
+
+\usepackage{url}
 
@@
 %If Title is too long, use \titlerunning
-%\titlerunning{Short Title}
+\titlerunning{Cross-Organizational Process Mining}
 
@@
 %\authorrunning{First Author et al.}
-\institute{Computer Engineering Department, Middle East Technical University, Turkey}
-%\email{yilmaz.onur@metu.edu.tr} 
+\institute{\email{\{onur.yilmaz, karagoz\}@ceng.metu.edu.tr} \\ Computer Engineering Department, Middle East Technical University, Turkey}
 %\email{karagoz@ceng.metu.edu.tr}
@@
 This approach is implemented as extensible and configurable plugin set in ProM framework and tested by synthetic and real life logs where successful and suitable results are achieved within evaluation metrics.
-Generated recommendation results indicate that the use of this approach considerably helps users to focus on the areas of process models with potential performance improvement, which are difficult to spot manually and visually.
+Generated recommendation results indicate that the use of this approach can help users to focus on the areas of process models with potential performance improvement, which are difficult to spot manually and visually.
 \end{abstract}
 
-\keywords{Process Mining, Cross-organizational Process Mining, Recommendation Generation, Process Performance Improvement}
+\keywords{Process Mining, Cross-organizational Process Mining, Performance Indicators, Clustering, Process Performance Improvement}
 
 \input{1_introduction/introduction.tex}
+\input{2_relatedwork/relatedwork.tex}
+\input{3_background/background.tex}
+\input{4_methodology/methodology.tex}
+\input{5_results_discussions/results_discussions.tex}
+\input{6_conclusion_future_work/conclusion_future_work.tex}
 
 \bibliographystyle{splncs03}
-\bibliography{references/references}
+\bibliography{7_references/references}
 

### 2015-09-15 4_methodology/methodology.tex
no message

@@
 Since the number of clusters are not known priori, k-means clustering is applied starting \textit{k} from 1 to the number of organizations.
-For each clustering with different number of clusters, SSE values are plotted and user is asked to select the appropriate cluster size.
+For each clustering with different number of clusters, \textit{Sum of Squared Error (SSE)} values are plotted and user is asked to select the appropriate cluster size.
 For the selected cluster size, clustering related information is used to generate recommendations in the further steps.
@@
 
-\subsection{Recommendation Generation}
+\subsection{Genarating Suggestions/Recommendations for Performance Improvement}
 \label{subsec:recommendation-generation}

### 2015-09-16 1_introduction/introduction.tex
no message

@@
 With this approach it is aimed to help business process management users to focus on the potentially important parts of their business maps.
-Proposed methodology is implemented in ProM framework \cite{verbeek2010prom} as a set of plugins corresponding for each stage and packaged under the name of \textit{CrossOrgProcMin} and tested on a synthetic and real-life event logs.
+Proposed methodology is implemented in ProM framework \cite{verbeek2010prom} as a set of plug-ins corresponding for each stage and packaged under the name of \textit{CrossOrgProcMin} and tested on a synthetic and real-life event logs.
 Performance of methodology is assessed with a set of defined evaluation metrics for each stage and resulting recommendations are presented to show how this approach helps users to focus on learning opportunities between organizations with a performance improvement potential.

### 2015-09-16 5_results_discussions/coselog-wabo/coselog-wabo.tex
no message

@@
 Dataset contains records of receiving phase for the building permit application process in 5 municipalities, which are comparable since activity labels in the different event logs refer to the same activities performed in five municipalities.
-In this dataset \cite{coselog-data}, there are total of 1214 cases and 2142 events with a variable distribution between event logs of municipalities and municipalities are used as organizational logs.
+In this dataset \cite{coselog-data}, there are 1214 cases and 2142 events with a variable distribution between event logs of municipalities and municipalities are used as organizational logs.
 
 \begin{itemize}
-  \item In \textit{Process Model Mining} stage, with 10\% of noise threshold, high fitness values are achieved; however, some of the process models like Municipality \#4 and \#5 resulted with low appropriateness values.
+  \item In \textit{Process Model Mining} stage, with 10 \% of noise threshold, high fitness values are achieved; however, some of the process models like Municipality \#4 and \#5 resulted with low appropriateness values.
   \item In \textit{Performance Indicator Analysis} stage, after calculating the performance indicators, municipalities are clustered and three clusters are created: Municipality \#1 is located in the first cluster; Municipality \#2 and \#4 are located in the second cluster; and Municipality \#3 and \#5 are grouped in to the last cluster.
-  \item In \textit{Mismatch Pattern Analysis} stage, it can be stated that as the similarity between process models of municipalities increases, number of mismatch patterns decreases on most of the cases.
-When further analyzed, it can be seen that Municipalities \#4 and \#5, which have significantly more complex process model compared to others, fails in spotting mismatch patterns according to \textit{graph-edit similarity}.
+  \item In \textit{Mismatch Pattern Analysis} stage, it can be stated that as the similarity between process models of municipalities increases, number of mismatch patterns decreases for most of the cases.
+When further analyzed, it can be seen that Municipalities \#4 and \#5, which have significantly more complex process models compared to others, fail in spotting mismatch patterns under \textit{graph-edit similarity}.
   \item In \textit{Recommendation Generation} stage, for different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:coselog-wabo-recommendation-generation-analysis} for the thresholds of 25 \%, 50 \% and 75 \% since these are the breaking points.
 For instance, cluster of Municipality \#1 performs worse in 6 indicators with the difference of 25 \% and on average 5 mismatch patterns are listed for each performance indicator.
-When it is compared to the total mismatch patterns of Municipality #1, which is 357, proposed approach helps significantly to the user for focusing performance improvement.
+When it is compared to the total mismatch patterns of Municipality \#1, which is 357, proposed approach helps significantly to the user for focusing performance improvement.
 	\begin{figure}
@@
 		\caption{Recommendation Generation analysis for Environmental Permit Application Process dataset (3 Clusters)}
-	  \label{fig:coselog-wabo-recommendation-generation-analysis-k3}
+	  \label{fig:coselog-wabo-recommendation-generation-analysis}
 	\end{figure}

### 2015-09-16 paper.tex
no message

@@
 
-\title{Recommendation Generation for Performance Improvement by using Cross-Organizational Process Mining}
+\title{Generating Performance Improvement Suggestions by using Cross-Organizational Process Mining}
 %If Title is too long, use \titlerunning
@@
 \begin{abstract}
-Process mining is a relatively young and developing research area with the main idea of discovering, monitoring and improving processes by extracting information from the event logs.
+Process mining is a relatively young and developing research area with the main idea of discovering, monitoring and improving processes by extracting information from event logs.
 With the increase of cloud computing and shared infrastructures, event logs of multiple organizations are available for analysis where cross-organizational process mining stands with the opportunity for organizations learning from each other.
 The approach proposed in this study mines process models of organizations and calculates performance indicators; followed by clustering of organizations based on performance indicators and finally spots mismatches between the process models to generate recommendations.
-This approach is implemented as extensible and configurable plugin set in ProM framework and tested by synthetic and real life logs where successful and suitable results are achieved within evaluation metrics.
-Generated recommendation results indicate that the use of this approach can help users to focus on the areas of process models with potential performance improvement, which are difficult to spot manually and visually.
+This approach is implemented as an extensible and configurable plug-in set in ProM framework and tested by synthetic and real life logs where successful and suitable results are achieved within evaluation metrics.
+Generated recommendation results indicate that the use of this approach can help users to focus on the parts of process models with potential performance improvement, which are difficult to spot manually and visually.
 \end{abstract}

### 2015-11-07 1_introduction/introduction.tex
no message

@@
 Traditional process mining approaches work on a single organization; however, with the increase of cloud computing and shared infrastructures, event logs of multiple organizations are currently available for analysis where cross-organizational process mining stands out.
-In cross-organizational process mining area, recent studies focus on commonality and collaboration between organizations, especially on how similar the process models and behaviors of organizations under cross comparison \cite{buijs2012towards} and challenges based on partitioning of tasks and process models between organizations \cite{van2011intra}.
-This study is based on the environment where processes are executed on several organizations and cross-organizational process mining is applied with the idea of unsupervised learning where predictor variables related to performances of organizations are used.
+In the cross-organizational process mining area, recent studies focus on commonality and collaboration between organizations, especially on how similar the process models and behaviors of organizations under cross comparison are \cite{buijs2012towards} and challenges based on partitioning of tasks and process models between organizations \cite{van2011intra}.
+This study is based on the environment where processes are executed in several organizations and cross-organizational process mining is applied with the idea of unsupervised learning where predictor variables related to performances of organizations are used.
 

### 2015-11-07 3_background/background.tex
no message

@@
 In this section, process discovery methods and mismatch patterns are presented within the scope of this work.
-In process mining field, various process discovery algorithms are proposed to address different challenges in process discovery and using different notations.
+In the process mining field, various process discovery algorithms are proposed to address different challenges in process discovery and using different notations.
 In this study, since the focus is learning lessons from cross-organizational mining, we used Inductive Process Mining \cite{leemans2013discovering} for process discovery, which is simple, highly applicable and configurable.

### 2015-11-07 4_methodology/methodology.tex
no message

@@
 Thirdly, in \textit{Mismatch Pattern Analysis}, differences between process models of organizations are extracted with well-established mismatch patterns.
-Finally, in \textit{Recommendation Generation}, using the performance indicator clusterings and differences between process models, a set of recommendations for each organization is generated.
+Finally, in \textit{Recommendation Generation}, using the performance indicator clusterings and differences between process models; a set of recommendations for each organization is generated.
 \begin{figure}
@@
 Process model mining in the proposed approach has the aim of creating reproducible and generalized process models from event logs.
-In order to achieve this aim, implementation of \textit{Inductive Miner Infrequent (IMi)}, which is proposed in \cite{leemans2014discoveringinfrequent} as an extension to \textit{Inductive Miner} to handle noise in the event logs, is used in this study.
+In order to achieve this aim, implementation of the \textit{Inductive Miner Infrequent (IMi)}, which is proposed in \cite{leemans2014discoveringinfrequent} as an extension to \textit{Inductive Miner} to handle noise in the event logs, is used in this study.
 In order to set a filtering threshold, a user-provided value between 0 to 1 is added as input to the method in addition to event logs.
@@
 \label{subsec:recommendation-generation}
-Recommendation generation stage in the methodology is the final and core stage where all information retrieved from event logs until now are utilized.
+Recommendation generation stage in the methodology is the final and core stage where all information retrieved from the event logs until now are utilized.
 In this study, idea of recommendation is based on providing a set of mismatch patterns for each organization so that they can enhance their processes.

### 2015-11-07 paper.tex
no message

@@
 The approach proposed in this study mines process models of organizations and calculates performance indicators; followed by clustering of organizations based on performance indicators and finally spots mismatches between the process models to generate recommendations.
-This approach is implemented as an extensible and configurable plug-in set in ProM framework and tested by synthetic and real life logs where successful and suitable results are achieved within evaluation metrics.
+This approach is implemented as an extensible and configurable plug-in set in ProM framework and tested by synthetic and real life logs where successful and suitable results are achieved with defined evaluation metrics.
 Generated recommendation results indicate that the use of this approach can help users to focus on the parts of process models with potential performance improvement, which are difficult to spot manually and visually.

### 2015-11-08 2_relatedwork/relatedwork.tex
no message

@@
 Cross-organizational mining is based on cross-correlation of workflows and the realized activities in different organization to compare in an objective approach.
-In the study of Bujis et al.
-\cite{buijs2012towards}, process models and behaviors of organizations are cross-compared with the idea of supporting and representing.
+In the study of Buijs et al.
+\cite{buijs2012towards}, process models and behaviors of organizations are cross-compared with the idea of supporting each other and representing differences.
 In the studies of van der Aalst \cite{van2011business,van2011intra}, configurable process models are proposed with the ideas of \textit{exploiting commonality} and \textit{collaboration} for the organizations sharing the same infrastructure and doing the similar work.

### 2015-11-11 2_relatedwork/relatedwork.tex
no message

@@
 
-Similarity in process mining have various approaches which focus on metrics \cite{dijkman2011similarity}, analytical comparison \cite{buijs2014comparing}, delta analysis \cite{esgin2011delta,esgin2013sequence} and mismatch patterns \cite{dijkman2007mismatch}.
+Similarity in process mining have various approaches which focus on metrics \cite{dijkman2011similarity}, analytical comparison \cite{buijs2014comparing,weidlich2011variability}, ontology analysis \cite{pascalau2010variants}, delta analysis \cite{esgin2011delta,esgin2013sequence,hallerbach2010variability} and mismatch patterns \cite{dijkman2007mismatch}.
 In this research, combination of metric and mismatch pattern approaches are used to identify variations between process models of different organizations that execute the same tasks.

### 2015-11-11 4_methodology/methodology.tex
no message

@@
 Process model mining in the proposed approach has the aim of creating reproducible and generalized process models from event logs.
-In order to achieve this aim, implementation of the \textit{Inductive Miner Infrequent (IMi)}, which is proposed in \cite{leemans2014discoveringinfrequent} as an extension to \textit{Inductive Miner} to handle noise in the event logs, is used in this study.
+Considering the fact that the process models may not be defined beforehand or outdated to reflect latest state of the process, they are mined from event logs.
+However, if there are process models that represent the event logs, this stage can be skipped.
+In order to mine process models, implementation of the \textit{Inductive Miner Infrequent (IMi)}, which is proposed in \cite{leemans2014discoveringinfrequent} as an extension to \textit{Inductive Miner} to handle noise in the event logs, is used in this study.
 In order to set a filtering threshold, a user-provided value between 0 to 1 is added as input to the method in addition to event logs.

### 2015-11-12 6_conclusion_future_work/conclusion_future_work.tex
no message

@@
 \begin{itemize}
-	\item In the process mining stage, instead of \textit{Inductive Miner}, different techniques can be used which can mine complex process models with higher appropriateness levels while keeping the current high fitness values.
+	\item In the process mining stage, instead of \textit{Inductive Miner}, new techniques can be used which can mine complex process models with higher appropriateness levels while keeping the current high fitness values.
 	\item In the performance indicator analysis stage, new indicators can be defined based on the business environment, event log attributes and user needs.

### 2015-11-21 4_methodology/methodology.tex
All formalization added

@@
 From the performance perspective, organizations want to minimize average time between activities to increase their throughput \cite{van2012replaying}.
+This notion can be defined as follows:
+  \theoremstyle{definition}
+  \begin{definition}{}
+  Average time between activity $A$ and $B$ in organization $i$ is $AvgTime_{A\rightarrow B}^{i} = \frac{\sum_{Case\ c \in Event Log_{i}} TimeBetween_{c}(A,B)}{|Occurences_{Event\ Log_{i}}(A,B)|}$ where
+    \begin{enumerate}
+      \item $TimeBetween_{c}(A, B) = EndTime_{c}(B) - StartTime_{c}(A)$
+      \item $StartTime_{c}(A)$ is start time of activity $A$ in case $c$,
+      \item $EndTime_{c}(B)$ is end time of activity $B$ in case $c$,
+      \item $|Occurences_{Event Log_{i}}(A, B)|$ is number of occurrences of activity $A$ followed by $B$ in  $Event\ Log_{i}$.
+    \end{enumerate}
+  \end{definition}
 	\item[Standard Deviation of Time Between Activities] Time between activities in real life is not stable and they deviate due to various reasons such as the user responsible of tasks, size and the content of tasks or seasonality \cite{van2011process}.
@@
 Minimized deviation in time helps organizations to plan, act and re-organize the activities in the processes with high accuracy \cite{van2012replaying}.
+With the same approach above, the following formulation can be defined:
+  \theoremstyle{definition}
+  \begin{definition}{}
+  Standard deviation time between activity $A$ and $B$ in organization $i$ is $StdDevTime_{A\rightarrow B}^{i} = \sqrt{\frac{\sum_{Case\ c \in Event Log_{i}} [TimeBetween_{c}(A, B) - AvgTime_{A\rightarrow B}^{i}]^{2}}{Occurences_{Event\ Log_{i}}(A,B)} }$
+  \end{definition}
 \end{description}
@@
 Replay of event logs on process models is based on the idea of \textit{alignment} which is formalized in \cite{van2012replaying} and the basic assumption in this concept is that process models and event logs have the same activity labels.
-For each organization, the steps of alignment and creating transitions are performed with the corresponding event logs and process models; and the resulting process summaries are used for further analysis.
+For each organization, the steps of alignment and creating transitions are performed with the corresponding event logs and process models; and the resulting process performance summaries are used for further analysis.
+Resulting data can be defined as follows:
+  \theoremstyle{definition}
+  \begin{definition}{} Performance Summary data for any organization $i$ is $PerfSum_{i}= \{AvgTimeSum_{i}\ \cup\ StdDevTimeSum_{i}\}$ where
+    \begin{enumerate}
+      \item $AvgTimeSum_{i} = \{ AvgTime_{A \rightarrow B}^{i} | A , B  \in Event\ Log_{i}\}$
+      \item $StdDevTimeSum_{i} = \{ StdDevTime_{ A\rightarrow B}^{i} | A, B  \in Event\ Log_{i}\}$
+    \end{enumerate}
+  \end{definition}
 
@@
 For the selected cluster size, clustering related information is used to generate recommendations in the further steps.
+Resulting cluster analysis data is formulated as follows:
+
+\theoremstyle{definition}
+\begin{definition}
+Cluster Analysis Data is a tuple $(k, Assignments, Cluster\ Centroids)$ where
+\begin{enumerate}
+  \item $k$ is the number of clusters,
+  \item $Assignments$ is a set of tuple $(Organization_{i}, Cluster_{j})$ where $i$ is identifier for organization and $j \leq k$ is identifier for cluster,
+  \item $Cluster\ Centroids$ is a set of tuple $(Cluster_{j}, Type, A_{start}, A_{end}, Value)$ where
+    \begin{enumerate}
+      \item $Type$ is performance indicator type which is $Average$ or $StandardDev$,
+      \item $A_{start}$ and $A_{end}$ are starting and ending points of performance indicator,
+      \item $Value$ is the actual value of performance indicator,
+      \item $Cluster\ Centroids_{j}$ is a function that returns a set of $Centroid$ which is a tuple $(Type, A_{start}, A_{end}, Value)$ for $Cluster_{j}$.
+    \end{enumerate} 
+\end{enumerate}
+\end{definition}
+
 This stage of methodology can be visualized as an input-output system in Figure~\ref{fig:performance-indicator-clustering-blackbox}. 
@@
 In other words, differences of process models are located through a starting activity to an ending activity.
+With this aim, each mismatch pattern and its analyzers are defined by extending the following definitions:
+\theoremstyle{definition}
+    \begin{definition}
+    Mismatch Pattern is a tuple ${Mismatch\ Patten} = (O_{1}, O_{2}, ExtensionData, A_{start}, A_{end}) $ where 
+    \begin{enumerate}
+      \item $O_{1}$ is the first organization and \item $O_{2}$ is the second organization in between the pattern occurs,
+      \item $ExtensionData$ is a set of tuples where mismatch related information is recorded, 
+      \item $A_{start}$ and $A_{end}$ are starting and ending points to check mismatch patterns.
+    \end{enumerate}
+    \end{definition}
+
+    \theoremstyle{definition}
+    \begin{definition}
+    Mismatch Pattern Analyzer is a function $MismatchPatternAnalyzer(O_{1}, O_{2}, A_{start}, A_{end})$ and it returns a set of \textit{Mismatch Pattern} for the organization $O_{1}$ compared to $O_{2}$ for the activities between $A_{start}$ and $A_{end}$.
+    \end{definition}
+
 For each organization, mismatch patterns are gathered and stored for the further analysis as visualized in Figure~\ref{fig:mismatch-pattern-analysis-blackbox}.
@@
 In addition, clustering of organizations is undertaken to generalize the way of identifying which organizations perform better in this environment.
+Recommendation idea and recommendation generation function is defined as following:
+\theoremstyle{definition}
+\begin{definition}
+Recommendation is a tuple ${Recommendation} = (O, A_{start}, A_{end}, Mismatch\ Patterns) $ where 
+  \begin{enumerate}
+    \item $O$ is identifier for organization,
+    \item $A_{start}$ and $A_{end}$ are starting and ending activities in between the recommendations are checked,
+    \item $Mismatch\ Patterns$ is collection of mismatch patterns.
+  \end{enumerate}
+\end{definition}
+
+\theoremstyle{definition}
+\begin{definition}
+Recommendation generation is a function that is $RecGen(O, C, P)$ and it returns a set of $Recommendation$ where
+  \begin{enumerate}
+    \item $O$ is identifier for organization,
+    \item $C$ is \textit{Cluster Analysis Data} which is result of cluster analysis stage,
+    \item $P$ is \textit{Performance Threshold} which is a real number larger than or equal to 0 and it is calculated over the same type of performance indicators of different organizations in \textit{Cluster Analysis Data}.
+  \end{enumerate}
+\end{definition}
 
@@
 Only mismatches which are located between the activities that causes high level of difference in performance indicators are analyzed.
+This approach is formalized in Algorithm~\ref{algo:recgen}.
+ \begin{algorithm}
+\DontPrintSemicolon % Some LaTeX compilers require you to use \dontprintsemicolon instead 
+\KwIn{$O$ organization, $C$ Cluster Analysis Data, $P$ performance difference threshold}
+\KwOut{$Recommendations$ a set of recommendations}
+$Recommendations \leftarrow \{\}$ \;
+$i \leftarrow C(Assignments(O))$ \;
+\For{$Centroid \in C(Cluster Centroids_{i})$} { 
+  \For{$Centroid' \in C(Cluster Centroids_{j})\ i\neq j$} { 
+    \If{$Centroid(A_{start}) = Centroid'(A_{start})\ \&\ Centroid(A_{end}) = Centroid'(A_{end})$} {
+      \If{ ($\left |  Centroid(Value) -  Centroid'(Value)\right | \div Centroid(Value)) \geq P$  } {
+        $A_{start} \leftarrow Centroid(A_{start})$ \;
+        $A_{end} \leftarrow Centroid(A_{end})$ \;
+        $MismatchPatterns \leftarrow \{\}$ \;
+        \For{$O' \in C(Assignments(j))$} {
+          $MismatchPatterns$ \leftarrow  Mismatch Pattern Analysis($O$,$O'$,$A_{start}$,$A_{end}$) \;
+        }
+        $Recommendations$ \leftarrow  Recommendation($O$,$A_{start}$,$A_{end}$, $MismatchPatterns$) \;
+      }
+    }
+  }
+}
+\Return{$Recommendations$} \;
+\caption{Recommendation Generation}
+\label{algo:recgen}
+\end{algorithm}
 

### 2015-11-21 5_results_discussions/coselog-wabo/coselog-wabo.tex
Remove itemize in discussion

@@
 
-\begin{itemize}
-  \item In \textit{Process Model Mining} stage, with 10 \% of noise threshold, high fitness values are achieved; however, some of the process models like Municipality \#4 and \#5 resulted with low appropriateness values.
-  \item In \textit{Performance Indicator Analysis} stage, after calculating the performance indicators, municipalities are clustered and three clusters are created: Municipality \#1 is located in the first cluster; Municipality \#2 and \#4 are located in the second cluster; and Municipality \#3 and \#5 are grouped in to the last cluster.
-  \item In \textit{Mismatch Pattern Analysis} stage, it can be stated that as the similarity between process models of municipalities increases, number of mismatch patterns decreases for most of the cases.
+In \textit{Process Model Mining} stage, with 10 \% of noise threshold, high fitness values are achieved; however, some of the process models like Municipality \#4 and \#5 resulted with low appropriateness values.
+In \textit{Performance Indicator Analysis} stage, after calculating the performance indicators, municipalities are clustered and three clusters are created: Municipality \#1 is located in the first cluster; Municipality \#2 and \#4 are located in the second cluster; and Municipality \#3 and \#5 are grouped in to the last cluster.
+In \textit{Mismatch Pattern Analysis} stage, it can be stated that as the similarity between process models of municipalities increases, number of mismatch patterns decreases for most of the cases.
 When further analyzed, it can be seen that Municipalities \#4 and \#5, which have significantly more complex process models compared to others, fail in spotting mismatch patterns under \textit{graph-edit similarity}.
-  \item In \textit{Recommendation Generation} stage, for different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:coselog-wabo-recommendation-generation-analysis} for the thresholds of 25 \%, 50 \% and 75 \% since these are the breaking points.
+In \textit{Recommendation Generation} stage, for different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:coselog-wabo-recommendation-generation-analysis} for the thresholds of 25 \%, 50 \% and 75 \% since these are the breaking points.
 For instance, cluster of Municipality \#1 performs worse in 6 indicators with the difference of 25 \% and on average 5 mismatch patterns are listed for each performance indicator.
@@
 \end{figure}
-\end{itemize}

### 2015-11-21 5_results_discussions/loan-application-process/loan-application-process.tex
no message
Remove itemize in discussion

@@
 
-\begin{itemize}
-  \item In \textit{Process Model Mining} stage, process models resulted with perfect fitness and high appropriateness as it is expected from a synthetically generated dataset without noise.
-  \item In \textit{Performance Indicator Analysis} stage, firstly event logs are replayed over process models and performance indicators are calculated and then organizations are clustered based on their performance indicators.
+In \textit{Process Model Mining} stage, process models resulted with perfect fitness and high appropriateness as it is expected from a synthetically generated dataset without noise.
+In \textit{Performance Indicator Analysis} stage, firstly event logs are replayed over process models and performance indicators are calculated and then organizations are clustered based on their performance indicators.
 In order to avoid overfitting,  with two clusters, Variant \#1, \#2, and \#4 are grouped into one cluster where only Variant \#3 is left to other cluster.
-  \item In \textit{Mismatch Pattern Analysis} stage, number of mismatch patterns are analyzed with the \textit{graph-edit similarity} between each two organization.
+In \textit{Mismatch Pattern Analysis} stage, number of mismatch patterns are analyzed with the \textit{graph-edit similarity} between each two organization.
 As the similarity between process models decreases our method spots more mismatch patterns and it ensures that the developed mismatch pattern analyzers work as expected for this dataset.
-  \item In \textit{Recommendation Generation} stage, for different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:loan-recommendation-generation-analysis}.
-    \begin{figure}
+In \textit{Recommendation Generation} stage, for different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:loan-recommendation-generation-analysis}.
+\begin{figure}[t!]
     	\centering
@@
 This shows the methodology proposed in this study can help users to focus on differences between organizations given this dataset.
-\end{itemize}

### 2015-11-21 4_methodology/methodology.tex
Remove itemize in discussion
Shortening in progress

@@
 Resulting cluster analysis data is formulated as follows:
-
 \theoremstyle{definition}
@@
 In this phase, differences between process models will be revealed by the mismatch patterns which are defined by Dijkman \cite{dijkman2007mismatch}.
-In the process mining stage, process models are mined to create Workflow nets; however, mismatch pattern definitions are closer to business environment and it is more suitable spot patterns in BPMN notation.
-Thus, mined process models are converted to BPMN models and then mismatch pattern analysis is applied in order to locate the differences between two process models or two clusters of process models.
-In addition, since performance indicators are calculated based on a starting and ending point in the process model, the same approach is applied to locate mismatch patterns.
+Since performance indicators are calculated based on a starting and ending point in the process model, the same approach is applied to locate mismatch patterns.
 In other words, differences of process models are located through a starting activity to an ending activity.
@@
     \end{definition}
+\theoremstyle{definition}
 
-    \theoremstyle{definition}
 \begin{definition}
@@
 \label{subsec:recommendation-generation}
+\theoremstyle{definition}
 Recommendation generation stage in the methodology is the final and core stage where all information retrieved from the event logs until now are utilized.
@@
 These mismatch patterns are generated by comparing the process models of other organizations, particularly those that are performing better in terms of their performance indicator values.
-In addition, clustering of organizations is undertaken to generalize the way of identifying which organizations perform better in this environment.
 Recommendation idea and recommendation generation function is defined as following:
-\theoremstyle{definition}
 \begin{definition}
@@
 This stage of methodology can be visualized as gathering inputs of mismatch patterns data and cluster analysis data in Figure~\ref{fig:recommendation-generation-blackox}.
-In addition, a performance difference threshold is gathered from the user to specify how much difference between clusters is necessary to check for mismatch patterns and generate recommendations.
-This stage generates recommendation data for each organization that contains a set of mismatch patterns.
 \begin{figure}

### 2015-11-21 4_methodology/methodology.tex
Shortening - in progress

@@
 In order to set a filtering threshold, a user-provided value between 0 to 1 is added as input to the method in addition to event logs.
-Black-box of this stage is illustrated in Figure~\ref{fig:process-model-mining-blackbox} and this stage is called for every organization's event logs to create their own process models in Workflow net formalization.
-\begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{4_methodology/process-model-mining-blackbox}
-  \caption{Process Model Mining Stage as Black-box }
-  \label{fig:process-model-mining-blackbox}
-\end{figure}
 
@@
 \end{algorithm}
-
 This stage of methodology can be visualized as gathering inputs of mismatch patterns data and cluster analysis data in Figure~\ref{fig:recommendation-generation-blackox}.

### 2015-11-21 6_conclusion_future_work/conclusion_future_work.tex
Shortening - in progress

@@
 Results show that it is possible to use cross-organizational process mining and mismatch patterns for performance improvement recommendations.
-In this study, a four-stage solution is presented and their performances are explained.
-In addition, proposed methodology is developed as extensible and configurable set of plugins in ProM framework \cite{verbeek2010prom} and published as open-source.
+In this study, proposed methodology is developed as extensible and configurable set of plugins in ProM framework \cite{verbeek2010prom} and published as open-source.
 This makes the methodology open to include new process mining methods, mismatch patterns and clustering approaches as well as testing with different datasets.

### 2015-11-21 4_methodology/methodology.tex
no message

--- 2015-11-21 4_methodology/methodology.tex
@@
 
-This stage of methodology can be visualized as an input-output system in Figure~\ref{fig:performance-indicator-clustering-blackbox}. 
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{4_methodology/performance-indicator-clustering-blackbox}
-  \caption{Performance Indicator Clustering Stage as Black-box }
-  \label{fig:performance-indicator-clustering-blackbox}
-\end{figure}
-
 \subsection{Mismatch Pattern Analysis}
@@
 \end{algorithm}
-This stage of methodology can be visualized as gathering inputs of mismatch patterns data and cluster analysis data in Figure~\ref{fig:recommendation-generation-blackox}.
-\begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{4_methodology/recommendation-generation-blackbox}
-  \caption{Recommendation Generation Stage as Black-box}
-  \label{fig:recommendation-generation-blackox}
-\end{figure}
 

### 2015-11-21 4_methodology/methodology.tex
no message

@@
 In other words, differences of process models are located through a starting activity to an ending activity.
-With this aim, each mismatch pattern and its analyzers are defined by extending the following definitions:
+With this aim, each mismatch pattern and its analyzers are defined by extending the following definitions.
+For each organization, mismatch pattern analyzers are pipelined and mismatch patterns are stored for further analysis.
 \theoremstyle{definition}
@@
 \end{definition}
-
-For each organization, mismatch patterns are gathered and stored for the further analysis as visualized in Figure~\ref{fig:mismatch-pattern-analysis-blackbox}.
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{4_methodology/mismatch-pattern-analysis-blackbox}
-  \caption{Mismatch Pattern Analysis Stage as Black-box}
-  \label{fig:mismatch-pattern-analysis-blackbox}
-\end{figure}
 

### 2015-11-21 5_results_discussions/results_discussions.tex
no message
Shortening

@@
-\section{Results and Discussions}
+\section{Experimental Analysis Results and Discussions}
 \label{sec:results-and-discussions}
@@
 Approach in this study is an aggregation of various methods and they are significantly different from each other in their mathematical background.
-Therefore, instead of a global evaluation metric for the complete methodology, each stage is evaluated within its evaluation metrics which are as follows:
-\begin{description}
-	\item[Process Model Mining] Performance of process mining stage is measured by \textit{fitness} and \textit{appropriateness} which are defined in \cite{rozinat2008conformance}.
-	\item[Performance Indicator Analysis] In replay phase, \textit{alignment costs} \cite{van2012replaying} are compared with process model mining metrics.
+Therefore, instead of a global evaluation metric for the complete methodology, each stage is evaluated within its evaluation metrics.
+In \textit{process model mining}, performance of process mining stage is measured by \textit{fitness} and \textit{appropriateness} which are defined in \cite{rozinat2008conformance}.
+In \textit{performance indicator analysis}, \textit{alignment costs} \cite{van2012replaying} are compared with process model mining metrics for replay phase.
 In clustering phase, \textit{within-SSE} analysis is undertaken to decide on the number of clusters.
-	\item[Mismatch Pattern Analysis] In this stage, number of mismatch patterns found are compared with the \textit{graph-edit similarity} \cite{dijkman2011similarity} of process models.
-	\item[Recommendation Generation] In recommendation generation, different threshold values are tried to check how many mismatch patterns are generated for organizations and how they could be used for focused analysis.
-\end{description}
+For \textit{mismatch pattern analysis}, number of mismatch patterns found are compared with the \textit{graph-edit similarity} \cite{dijkman2011similarity} of process models.
+In \textit{recommendation generation}, different threshold values are tried to check how many mismatch patterns are generated for organizations and how they could be used for focused analysis.
 

### 2015-11-21 4_methodology/methodology.tex
no message

@@
 However, in this study, process related performance values are considered since differences in the process models are studied in the next stages.
-To this aim, the following performance indicators are calculated and analyzed in this stage of methodology:
+To this aim, the following performance indicators are calculated:
 \begin{description}
-	\item[Average Time Between Activities] For each activity in the process model, average time to reach the next activity is calculated.
-This is a simple but powerful performance metric for organizations since it can yield the average time to complete one task based on a starting point.
+	\item[Average Time Between Activities] This is a simple but powerful performance metric for organizations since it can yield the average time to complete one task based on a starting point.
 From the performance perspective, organizations want to minimize average time between activities to increase their throughput \cite{van2012replaying}.
@@
 \theoremstyle{definition}
-
 \begin{definition}
@@
 Algorithm of recommendation generation function is based on the idea of checking other clusters for a significant change in performance indicators, where significance is defined by the threshold provided by user.
-After finding significant difference, all organizations in other clusters are checked against mismatch patterns with the starting and ending activities defined in performance indicators.
 Only mismatches which are located between the activities that causes high level of difference in performance indicators are analyzed.
